---
title: "Photosynthesis"
author: "AnaisLebrun"
date: "2023-04-14"
output: html_document
---

In this document are presented the individual incubations data from the mesocosm experiment that took place in Tromso in summer 2022. Two species were investigated : *Saccharina latissima* (SL) and *Alaria esculenta* (AE). Each species have been incubated at $T_{0}$, during the experiment and at $T_{F}$.

```{r setup, include=FALSE, warning=FALSE}
library(Rcpp)
library(readxl)
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(broom)
library(stargazer)
library(marelac)
library(lubridate)
library(Rcpp)
library(stringr)
library(magick)
library(cowplot)
library(gridExtra)
library(forcats)
library(ggpubr)
library(firatheme)
library(seacarb)
library(tidyverse)
library(rstatix)
library(lme4)
library(ggpubr)
library(emmeans)
#O2_raw_1 <- read_excel("/Users/anaislebrun/Desktop/These/Meso NYA 2021/O2/data/O2_individual_incubations.xlsx", 
                                             #col_types = c("text","text", "text","text","text", #"text", "date", "text", "numeric", "text","text", "numeric", "text", "numeric","numeric", "numeric", "numeric"))

#O2_raw_1<-drop_na(O2_raw_1, c(Salinity,Temp))
#PAR_export <- read_excel("/Users/anaislebrun/Desktop/These/Meso NYA 2021/O2/data/PAR_data.xlsx", 
     #sheet = "Feuil2", col_types = c("date","numeric", "numeric", "numeric", "numeric"))
```

Let's look at the temperature within time for each condition. 

```{r setup, include=FALSE, warning=FALSE}
temperature <- read_excel("data/temperature.xlsx", 
     col_types = c("date", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric"))

temperature$date<-temperature$...1
temperature<-temperature[,-1]
#temperature<-separate(col=date,c("date","time")," ",data=temperature)

library(dplyr)
library(lubridate)
library(naniar)

hour_temperature<-temperature %>% 
  mutate(date = ymd_hms(date), dt = as_date(date), hr = hour(date)) %>% 
  group_by(dt, hr) %>% 
  filter(date == min(date)) %>% 
  replace_with_na_all(condition = ~.x <= 0)%>% 
  ungroup()

hour_temperature$C0<-rowMeans(hour_temperature[,1:3])
hour_temperature$C1<-rowMeans(hour_temperature[,4:6])
hour_temperature$C2<-rowMeans(hour_temperature[,7:9])
hour_temperature$C3<-rowMeans(hour_temperature[,10:12])


Temperature_plot<-ggplot(hour_temperature,aes(x=date))+
  geom_point(aes(y=C3),color="#901C21")+geom_line(aes(y=C3),size=3,color="#901C21",alpha=0.4)+
  geom_point(aes(y=C2),color="#FC1D28")+geom_line(aes(y=C2),size=3,color="#FC1D28",alpha=0.4)+
  geom_point(aes(y=C1),color="#E48121")+geom_line(aes(y=C1),size=3,color="#E48121",alpha=0.4)+
  geom_point(aes(y=C0),color="#92c5de")+ geom_line(aes(y=C0),size=3,color="#92c5de",alpha=0.4)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  labs(x="time",y="Temperature (°C)")

jpeg(filename = "figures/Temperature_plot.jpeg",width=950, height=650)
Temperature_plot
dev.off()

delta_temperature<-hour_temperature %>% 
  summarise(deltaC1=C1-C0,deltaC2=C2-C0,deltaC3=C3-C0)

delta_temperature$date<-hour_temperature$date
delta_temperature_plot<-ggplot(delta_temperature,aes(x=date))+
  geom_point(aes(y=deltaC3),color="#901C21")+geom_line(aes(y=deltaC3),size=3,color="#901C21",alpha=0.4)+
  geom_point(aes(y=deltaC2),color="#FC1D28")+geom_line(aes(y=deltaC2),size=3,color="#FC1D28",alpha=0.4)+
  geom_point(aes(y=deltaC1),color="#E48121")+geom_line(aes(y=deltaC1),size=3,color="#E48121",alpha=0.4)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  labs(x="time",y="Delta Temperature (°C)")

jpeg(filename = "figures/delta_temperature_plot.jpeg",width=950, height=650)
delta_temperature_plot
dev.off()


```

Here are plotted all the raw $O_{2}$ measurements (1 measurement/minute) from the individual incubations. Most of them lasted 30 min, some lasted 60 min.

```{r raw data,echo=FALSE,warning=FALSE,fig.width=15,fig.height=15}

# graph O2 concentration with time for each ID
ggplot(O2_raw_1,aes(dt,O2))+
  geom_point(aes(group=grp,color=week))+
  geom_line(aes(group=grp))+
  theme_fira()+
  facet_wrap(~ID+species)+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        legend.title = element_text(size = rel(1.5), face = "bold"),
        plot.title = element_text(size=30, face="bold.italic",hjust = 0.5))+
  ggtitle("O2 curves before cleaning")
```

## 1° Data cleaning

During a light incubation of any photosynthetic organisms, $O_{2}$ progressively increase with time if photosynthesis occurs. However, for some reasons we can sometimes see outliers in the $O_{2}$ measurement. Theses outliers need to be remove before any analysis. This is the purpose of this 1st step.

Here are plotted the raw $O_{2}$ measurements after removal of the outliers. We removed : 1) complete graphs when values are way too high &/or variable, 2) all values after 30min of incubations, 3) the first 5mins of incubation, 4) ponctual measurement not following the general trend of a graph.

```{r O2 cleaning,echo=FALSE,warning=FALSE,fig.width=15,fig.height=15}

# A) Remove complete graph when values are way too high & variable
Weird_graphs<-O2_raw_1 %>%
  filter(ID==140 & week=="Week3" 
         |ID==54 & week=="Week2" 
         |ID==68 & week=="Week2" 
         |ID==73 & week=="Week3"
         |ID==52 & week=="Week2")

O2_raw_1 <- anti_join(O2_raw_1,
                            Weird_graphs, by = c("ID","week"))
rm(Weird_graphs)

# B) Remove all values after 30min of incubations
O2_raw_1 <- subset(O2_raw_1, dt<=1800)

# C) Remove the first 5 mins of incubation for each incubation
O2_raw_1 <- subset(O2_raw_1, dt>=300)

# D) Point by point: Remove each point not following the general trend
Weird_values<-O2_raw_1 %>%
  filter(ID==138 & week=="Week3" & dt<=180.00
    |ID==138 & week=="Week3" & dt>=660 & dt<=960 
    |ID==138 & week=="Week3" & dt>=1140 & dt<=1440
    |ID==139 & week=="Week3" & dt<=60
    |ID==139 & week=="Week3" & dt>=240 & dt<=780
    |ID==142 & week=="TF" & dt>=1680
    |ID==18 & week=="Week4" & dt>=1260
    |ID==36 & week=="Week4" & dt>=1260
    |ID==26 & week=="Week4" & dt>=1500 & dt<=1620
    |ID==28 & week=="Week4" & dt>=1500 & dt<=1620
    |ID==28 & week=="TF" & dt>=600 & dt<=660
    |ID==28 & week=="TF" & dt>=1320 & dt<=1380
    |ID==68 & week=="TF" & dt<=120
    |ID==7 & week=="Week1" & dt<=120
    |ID==76 & week=="Week3" & dt>=600 & dt<=780
    |ID==76 & week=="Week3" & dt>=1080 & dt<=1260
    |ID==77 & week=="Week3" & dt>=0 & dt<=240
    |ID==78 & week=="Week3" & dt>=1740
    |ID==8 & week=="T0" & dt<= 180
    |ID==81 & week=="Week3" & dt>=1440 & dt<=1500
    |ID==81 & week=="Week3" & dt>=1620
    |ID==82 & week=="Week3" & dt>=1680
    |ID==86 & week=="TF" & dt<=120
    |ID==89 & week=="Week3" & dt<=120
    |ID==90 & week=="Week2" & dt>=60 & dt<=120
    |ID==93 & week=="Week2" & dt<=240
    |ID==93 & week=="Week2" & dt>=1560
    |ID==93 & week=="Week2" & dt>=600 & dt<=720
    |ID==94 & week=="Week2" & dt<=240
    |ID==94 & week=="Week2" & dt>=1560
    |ID==94 & week=="Week2" & dt>=600 & dt<=720
    |ID==93 & week=="Week5" & dt<=60
    |ID==93 & week=="Week5" & dt>=300 & dt<=540
    |ID==93 & week=="Week5" & dt>=1500
    |ID==94 & week=="Week5" & dt<=60
    |ID==94 & week=="Week5" & dt>=300 & dt<=540
    |ID==94 & week=="Week5" & dt>=1500)

O2_raw_1 <- anti_join(O2_raw_1,
                            Weird_values, by = "dt")
rm(Weird_values)
# graph O2 concentration with time for each ID
ggplot(O2_raw_1,aes(dt,O2))+
  geom_point(aes(group=grp,color=week))+
  geom_line(aes(group=grp))+
  theme_fira()+
  facet_wrap(~ID+species)+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        legend.title = element_text(size = rel(3.5), face = "bold"),
        plot.title = element_text(size=30, face="bold.italic",hjust = 0.5),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(1, 'cm'), #change legend key width 
        legend.text = element_text(size=10))+
  scale_fill_discrete(limits = c("T0","Week 1","Week 2","Week 3","Week 4","Week 5","TF"))+#change legend text font size+
  ggtitle("O2 curves after cleaning")

```

A second step  is to check the temperature measurements during the incubation. Indeed the temperature influences the O2 calculation. Therefore, it is important to verify that the values of the temperatures used in the calculation do not seem aberrant.

```{r Temperature cleaning,echo=FALSE,warning=FALSE,fig.width=15,fig.height=15}
ggplot(O2_raw_1,aes(dt,Temp))+
  geom_point(aes(group=grp,color=week))+
  geom_line(aes(group=grp))+
  theme_fira()+
  facet_wrap(~ID+species)+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        legend.title = element_text(size = rel(1.5), face = "bold"),
        plot.title = element_text(size=30, face="bold.italic",hjust = 0.5))+
  ggtitle("Temperature during incubation")
```

The temperature data look good. We don't have to remove any outliers.

## 2° Model & slopes calculation

The second step is to calculate the slope of $O_{2}$ from T0 to TF based on a linear model to obtain the $\Delta(O_{2}$).

```{r Model,echo=FALSE,warning=FALSE,results=FALSE,fig.show='hide'}
LM<- O2_raw_1 %>%
  group_by(grp) %>%
  do(broom::tidy(lm(O2~dt, .)))

LM<-LM[LM$term=="dt",]
O2_raw <- merge(O2_raw_1, LM, by = 'grp')
O2_raw <- O2_raw %>% distinct(estimate, .keep_all = TRUE)

# graph O2 with model per grp
ggplot(O2_raw_1,aes(dt,O2))+
  geom_point(aes(group=grp),color="grey60")+
  geom_line(aes(group=grp))+
  geom_smooth(aes(group=grp),method="lm",formula="y ~ x")+
  stat_regline_equation() +
  theme_minimal()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        legend.title = element_text(size = rel(1.5), face = "bold"))+
  facet_wrap(ID~week)

O2_raw_1_93<-O2_raw_1[O2_raw_1$ID=="93",]
O2_raw_1_93<-O2_raw_1_93[O2_raw_1_93$week=="Week2",]
ggplot(O2_raw_1_93,aes(dt,O2))+
  geom_point(aes(group=grp),color="grey60")+
  geom_line(aes(group=grp))+
  geom_smooth(aes(group=grp),method="lm",formula="y ~ x")+
  stat_regline_equation() +
  theme_minimal()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        legend.title = element_text(size = rel(1.5), face = "bold"))

```

## 3° Normalization <br>

The third step is to normalize the $O_{2}$(µmol.L) rate with the biomass of the individual.

$$
normalizedO_{2} (umol.g(dw)^-.^1min^-.^1) =  \frac{O_{2} (umol/L.min) * V(L)} {Biomass (g)}
$$ <br> with V = Volume of the chamber, in L (V=30L in our case) <br>

In our case we used the dry weight (g). Each individual has been weighted before each incubation. We use a regression relation between the wet & the dry weight to calculate the dry weight from the wet one at each incubation time.

## 4° O2 Results <br>

```{r Normalization & O2 results, echo=FALSE, warning=FALSE, message=FALSE, results=FALSE,fig.width=15,fig.height=10}

# Data manipulation ####
# Pull PAR & O2 measurements
# PAR in umol photons m-2 s-1. 
O2_raw_1$DateTime<-paste(O2_raw_1$date,O2_raw_1$time) # create 1 column DateTime
O2_raw_1$DateTime<-as_datetime(O2_raw_1$DateTime)
O2_raw_1$DateTime_rounded<-lubridate::round_date(
  O2_raw_1$DateTime,
  unit = "10 min") # approximate the time to within 10min
O2<- merge(O2_raw_1, PAR_export, by = "DateTime_rounded") # merge O2 & PAR data
O2$PAR<-0
O2$PAR[O2$condition == "T0"] <- O2$C0[O2$condition == "T0"]
O2$PAR[O2$condition == "C0"] <- O2$C0[O2$condition == "C0"]
O2$PAR[O2$condition == "C1"] <- O2$C1[O2$condition == "C1"]
O2$PAR[O2$condition == "C2"] <- O2$C2[O2$condition == "C2"]
O2$PAR[O2$condition == "C3"] <- O2$C3[O2$condition == "C3"]

#Calculate the dry weight using a regression formula 
# SL
SL<-O2_raw[O2_raw$species=="SL",]
SL$Dry_weight<-(SL$wet_weight*0.1664)+0.1548
# AE
AE<-O2_raw[O2_raw$species=="AE",]
AE$Dry_weight<-(AE$wet_weight*0.2614)-3.1997
# LD
LD<-O2_raw[O2_raw$species=="LD",]
LD$Dry_weight<-(LD$wet_weight*0.1359)+6.8917

O2_raw<-rbind(SL,AE,LD)
rm(SL,AE,LD)

#O2_PAR<-O2 %>%
#  select(grp,condition,replicate,mesocosm,species,week,Dry_weight,ID,PAR,O2) %>%
#  group_by(grp,condition,replicate,mesocosm,species,week,Dry_weight,ID)%>%
#  summarise(PAR = mean(PAR)/(length(PAR)*10*60)) #mean of PAR (within the incubation) and PAR converted in seconds

#O2_PAR<-O2 %>%
#  select(grp,condition,replicate,mesocosm,species,week,ID,PAR,O2) %>%
#  group_by(grp,condition,replicate,mesocosm,species,week,ID)%>%
#  summarise(PAR = sum(PAR)*60/(length(PAR))*10^-3) #Mean PAR received per min in umol photons m-2.min-1

#->O2_PAR$PAR 
# On ne divise pas par le PAR car Pi curves ne montrent pas un effet de la lumière


# Remove the Blank (= control incubation with only seawater in the chamber)
O2 <- O2[O2$species!="Blank",]
# Do the mean of the O2 rate per incubation
O2_mean<-O2_raw %>%
  select(grp,condition,replicate,mesocosm,species,week,Dry_weight,ID,estimate,std.error,Salinity) %>%
  group_by(grp,condition,replicate,mesocosm,species,week,Dry_weight,ID,Salinity)%>%
  summarise(estimate = mean(estimate))
Std_O2_mean<-O2_raw %>%
  select(grp,condition,replicate,mesocosm,species,week,Dry_weight,ID,estimate,std.error,Salinity) %>%
  group_by(grp,condition,replicate,mesocosm,species,week,Dry_weight,ID,Salinity)%>%
  summarise(std.error = mean(std.error))
# Do the mean of T° per incubation
#Temp<-O2 %>%
#  select(grp,condition,replicate,mesocosm,species,week,ID,Salinity,Temp) %>%
#  group_by(grp,condition,replicate,mesocosm,species,week,ID,Salinity)%>%
#  summarise(Temp = mean(Temp))

O2<-merge(O2_mean,Std_O2_mean,by=c("grp","condition","replicate","species","mesocosm","Dry_weight","ID","Salinity","week"))

#O2_PAR<-drop_na(O2_PAR)
#O2_raw$PAR<-O2_PAR$PAR
#O2<-O2_raw
#rm(O2_mean,O2_raw,O2_raw_1,PAR_export,LM)

# Divide O2 by the dry weight (*0.001 to convert it in kg) and multiply it by the volume of the chamber (V=30L)
# Rq : To do so, we separate the dataframe per weeks to avoid mixing data (which happens without doing this)
# Rq 2 : the std of the LM is subject to the same calculation

T0 <- O2[O2$week=="T0",]
T0$O2_normalized<-T0$estimate*30/T0$Dry_weight
T0$variance<-T0$std.error^2
T0$variance<-T0$variance*30/T0$Dry_weight
T0$std_normalized<-sqrt(T0$variance)

Week1 <- O2[O2$week=="Week1",]
Week1$O2_normalized<-Week1$estimate*30/Week1$Dry_weight
Week1$variance<-Week1$std.error^2
Week1$variance<-Week1$variance*30/Week1$Dry_weight
Week1$std_normalized<-sqrt(Week1$variance)

Week2 <- O2[O2$week=="Week2",]
Week2$O2_normalized<-Week2$estimate*30/Week2$Dry_weight
Week2$variance<-Week2$std.error^2
Week2$variance<-Week2$variance*30/Week2$Dry_weight
Week2$std_normalized<-sqrt(Week2$variance)

Week3 <- O2[O2$week=="Week3",]
Week3$O2_normalized<-Week3$estimate*30/Week3$Dry_weight
Week3$variance<-Week3$std.error^2
Week3$variance<-Week3$variance*30/Week3$Dry_weight
Week3$std_normalized<-sqrt(Week3$variance)

Week4 <- O2[O2$week=="Week4",]
Week4$O2_normalized<-Week4$estimate*30/Week4$Dry_weight
Week4$variance<-Week4$std.error^2
Week4$variance<-Week4$variance*30/Week4$Dry_weight
Week4$std_normalized<-sqrt(Week4$variance)

Week5 <- O2[O2$week=="Week5",]
Week5$O2_normalized<-Week5$estimate*30/Week5$Dry_weight
Week5$variance<-Week5$std.error^2
Week5$variance<-Week5$variance*30/Week5$Dry_weight
Week5$std_normalized<-sqrt(Week5$variance)

TF <- O2[O2$week=="TF",]
TF$O2_normalized<-TF$estimate*30/TF$Dry_weight
TF$variance<-TF$std.error^2
TF$variance<-TF$variance*30/TF$Dry_weight
TF$std_normalized<-sqrt(TF$variance)

O2<-rbind(T0, Week1, Week2, Week3, Week4, Week5, TF)
rm(T0, Week1, Week2, Week3, Week4, Week5, TF)

# Normalize the O2 rate with PAR
#O2$O2_normalized_PAR=O2$O2_normalized/O2$PAR
#O2$variance_2<-O2$std_normalized^2
#O2$variance<-O2$variance/O2$PAR
#O2$std_normalized_2<-sqrt(O2$variance)

# Define the order of apparition the x axis
O2$condition <- fct_relevel(O2$condition, c("T0", "C0","C1","C2","C3"))

# Divide the dataframe in 3 (1 for each species)
Alaria<-O2[O2$species=="AE",]
Laminaria<-O2[O2$species=="LD",]
Saccharina<-O2[O2$species=="SL",]

# For each new data frame: duplicate the rows corresponding to T0 incubation into incorporate the T0 values in each facet (cf- ggplot below)
# Alaria
Alaria_w2<-Alaria[rep(c(1:5),),]
Alaria_w2$Graph<-"Week2"
Alaria_w5<-Alaria[rep(c(1:5),),]
Alaria_w5$Graph<-"Week5"
Alaria_TF<-Alaria[rep(c(1:5),),]
Alaria_TF$Graph<-"TF"
Alaria<-Alaria[Alaria$week!="T0",]
Alaria$Graph<-Alaria$week
Alaria<-rbind(Alaria,Alaria_w2,Alaria_w5,Alaria_TF)
rm(Alaria_w2,Alaria_w5,Alaria_TF)
# Laminaria
Laminaria_w3<-Laminaria[rep(c(1:5),),]
Laminaria_w3$Graph<-"Week3"
Laminaria_TF<-Laminaria[rep(c(1:5),),]
Laminaria_TF$Graph<-"TF"
Laminaria<-Laminaria[Laminaria$week!="T0",]
Laminaria$Graph<-Laminaria$week
Laminaria<-rbind(Laminaria,Laminaria_w3,Laminaria_TF)
rm(Laminaria_w3,Laminaria_TF)
# Saccharina
Saccharina_w1<-Saccharina[rep(c(1:5),),]
Saccharina_w1$Graph<-"Week1"
Saccharina_w4<-Saccharina[rep(c(1:5),),]
Saccharina_w4$Graph<-"Week4"
Saccharina_TF<-Saccharina[rep(c(1:5),),]
Saccharina_TF$Graph<-"TF"
Saccharina<-Saccharina[Saccharina$week!="T0",]
Saccharina$Graph<-Saccharina$week
Saccharina<-rbind(Saccharina,Saccharina_w1, Saccharina_w4, Saccharina_TF)
rm(Saccharina_w1, Saccharina_w4, Saccharina_TF)
# Create a condition_week column
Alaria$condition_week<-paste(Alaria$condition,Alaria$week,sep="_")
Laminaria$condition_week<-paste(Laminaria$condition,Laminaria$week,sep="_")
Saccharina$condition_week<-paste(Saccharina$condition,Saccharina$week,sep="_")

# Define the order of apparition on the facet
Alaria$condition_week <- fct_relevel(Alaria$condition_week, c("T0_T0", "C0_Week2","C0_Week5","C0_TF","C1_Week2","C1_Week5","C1_TF","C2_Week2","C2_Week5","C2_TF","C3_Week2","C3_Week5","C3_TF"))
Laminaria$condition_week <- fct_relevel(Laminaria$condition_week, c("T0_T0", "C0_Week3","C0_TF","C1_Week3","C1_TF","C2_Week3","C2_TF","C3_Week3","C3_TF"))
Saccharina$condition_week <- fct_relevel(Saccharina$condition_week, c("T0_T0", "C0_Week1","C0_Week4","C0_TF","C1_Week1","C1_Week4","C1_TF","C2_Week1","C2_Week4","C2_TF","C3_Week1","C3_Week4","C3_TF"))

# Plot ####
# New color

# AE
AE_plot<-ggplot(Alaria,aes(y=O2_normalized,x=condition_week,colour=condition))+
  geom_point(size=3)+ 
  geom_errorbar(aes(ymin=O2_normalized-std_normalized, ymax=O2_normalized+std_normalized), width=.2,position=position_dodge(0.05))+
  scale_colour_manual(values=c("#cccccc","#92c5de","#0571b0","#f4a582","#ca0020"))+
  ylab(bquote('µmol O2'(min^-1,FW^-1)))+
  xlab(bquote('conditions'))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold", hjust=0.5),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.022),expand = expansion(mult = c(0,0)))+
  scale_x_discrete(labels= c("T0","Week 2", "Week 5","TF","Week 2", "Week 5","TF","Week 2", "Week 5","TF","Week 2", "Week 5","TF"))+
  annotate("rect", xmin = 0, xmax = 1.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 1.5, xmax = 4.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("rect", xmin = 4.5, xmax = 7.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 7.5, xmax = 10.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("rect", xmin = 10.5, xmax = 13.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("text", x = 3 + 3*(0:3), y = 0.01, label = c("C0","C1","C2","C3"), size = 4.5)+labs(caption = "AE")

# LD
LD_plot<-ggplot(Laminaria,aes(y=O2_normalized,x=condition_week,colour=condition))+
  geom_point(size=3)+ 
  geom_errorbar(aes(ymin=O2_normalized-std_normalized, ymax=O2_normalized+std_normalized), width=.2,position=position_dodge(0.05))+
  scale_colour_manual(values=c("#cccccc","#92c5de","#0571b0","#f4a582","#ca0020"))+
  ylab(bquote('µmol O2'(min^-1,FW^-1)))+
  xlab("conditions")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold", hjust=0.5),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.022),expand = expansion(mult = c(0,0)))+
  scale_x_discrete(labels= c("T0","Week 3","TF","Week 3","TF","Week 3","TF","Week 3","TF"))+
  annotate("rect", xmin = 0, xmax = 1.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 1.5, xmax = 3.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("rect", xmin = 3.5, xmax = 5.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 5.5, xmax = 7.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("rect", xmin = 7.5, xmax = 9.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("text", x = 2.5 + 2*(0:3), y =  0.01, label = c("C0","C1","C2","C3"), size = 4.5)+labs(caption = "LD")


# SL
SL_plot<-ggplot(Saccharina,aes(y=O2_normalized,x=condition_week,colour=condition))+
  geom_point(size=3)+ 
  geom_errorbar(aes(ymin=O2_normalized-std_normalized, ymax=O2_normalized+std_normalized), width=.2,position=position_dodge(0.05))+
  scale_colour_manual(values=c("#cccccc","#92c5de","#0571b0","#f4a582","#ca0020"))+
  ylab(bquote('µmol O2'(min^-1,FW^-1)))+
  xlab("conditions")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold", hjust=0.5),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.022),expand = expansion(mult = c(0,0)))+
  scale_x_discrete(labels= c("T0","Week 1", "Week 4","TF","Week 1", "Week 4","TF","Week 1", "Week 4","TF","Week 1", "Week 4","TF"))+
  annotate("rect", xmin = 0, xmax = 1.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 1.5, xmax = 4.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("rect", xmin = 4.5, xmax = 7.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 7.5, xmax = 10.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("rect", xmin = 10.5, xmax = 13.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("text", x = 3 + 3*(0:3), y = 0.015, label = c("C0","C1","C2","C3"), size = 4.5)+
  labs(caption = "SL")
  

figure <- ggarrange(AE_plot, SL_plot, LD_plot,
                    labels = c("AE", "SL", "LD"),
                    ncol = 1, nrow = 3,legend = NULL)
figure


#
Alaria$week_condition <- fct_relevel(Alaria$condition_week, c("T0_T0", "C0_Week2","C1_Week2","C2_Week2","C3_Week2","C0_Week5","C1_Week5","C2_Week5","C3_Week5","C0_TF","C1_TF","C2_TF","C3_TF"))
Laminaria$week_condition <- fct_relevel(Laminaria$condition_week, c("T0_T0", "C0_Week3","C1_Week3","C2_Week3","C3_Week3","C0_TF","C1_TF","C2_TF","C3_TF"))
Saccharina$week_condition <- fct_relevel(Saccharina$condition_week, c("T0_T0", "C0_Week1","C1_Week1","C2_Week1","C3_Week1","C0_Week4","C1_Week4","C2_Week4","C3_Week4","C0_TF","C1_TF","C2_TF","C3_TF"))

# Plot 2 #####
AE_plot<-ggplot(Alaria,aes(y=O2_normalized,x=week_condition,colour=condition))+
  geom_point(size=3)+ 
  geom_errorbar(aes(ymin=O2_normalized-std_normalized, ymax=O2_normalized+std_normalized), width=.2,position=position_dodge(0.05))+
  scale_colour_manual(values=c("#747676","#92c5de","#0571b0","#f4a582","#ca0020"))+
  ylab(bquote('µmol O2'(min^-1,FW^-1)))+
  xlab(bquote('conditions'))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold", hjust=0.5),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.022),expand = expansion(mult = c(0,0)))+
  scale_x_discrete(labels= c("T0","C0", "C1","C2","C3","C0", "C1","C2","C3","C0", "C1","C2","C3"))+
  annotate("rect", xmin = 0, xmax = 1.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 1.5, xmax = 5.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("rect", xmin = 5.5, xmax = 9.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 9.5, xmax = 13.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("text", x = 3.5 + 4*(0:2), y = 0.01, label = c("Week2","Week5","TF"), size = 6)+labs(caption = "AE")

# LD
LD_plot<-ggplot(Laminaria,aes(y=O2_normalized,x=week_condition,colour=condition))+
  geom_point(size=3)+ 
  geom_errorbar(aes(ymin=O2_normalized-std_normalized, ymax=O2_normalized+std_normalized), width=.2,position=position_dodge(0.05))+
  scale_colour_manual(values=c("#747676","#92c5de","#0571b0","#f4a582","#ca0020"))+
  ylab(bquote('µmol O2'(min^-1,FW^-1)))+
  xlab("conditions")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold", hjust=0.5),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.022),expand = expansion(mult = c(0,0)))+
  scale_x_discrete(labels= c("T0","C0", "C1","C2","C3","C0", "C1","C2","C3"))+
  annotate("rect", xmin = 0, xmax = 1.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 1.5, xmax = 5.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("rect", xmin = 5.5, xmax = 9.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("text", x = 3.5 + 4*(0:1), y =  0.015, label = c("Week3","TF"), size = 6)+labs(caption = "LD")


# SL
SL_plot<-ggplot(Saccharina,aes(y=O2_normalized,x=week_condition,colour=condition))+
  geom_point(size=3)+ 
  geom_errorbar(aes(ymin=O2_normalized-std_normalized, ymax=O2_normalized+std_normalized), width=.2,position=position_dodge(0.05))+
  scale_colour_manual(values=c("#747676","#92c5de","#0571b0","#f4a582","#ca0020"))+
  ylab(bquote('µmol O2'(min^-1,FW^-1)))+
  xlab("conditions")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold", hjust=0.5),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.022),expand = expansion(mult = c(0,0)))+
  scale_x_discrete(labels= c("T0","C0", "C1","C2","C3","C0", "C1","C2","C3","C0", "C1","C2","C3"))+
  annotate("rect", xmin = 0, xmax = 1.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 1.5, xmax = 5.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("rect", xmin = 5.5, xmax = 9.5, ymin = -0.01, ymax = 0.022, alpha = .1)+
  annotate("rect", xmin = 9.5, xmax = 13.5, ymin = -0.01, ymax = 0.022, alpha = .4)+
  annotate("text", x = 3.5 + 4*(0:2), y = 0.015, label = c("Week1","Week4","TF"), size = 6)+labs(caption = "SL")
  

# Statistics ####
#Robert : "What ultimately is it that you are wanting to test? If it is the difference in photosynthetic rates under different treatments and PAR conditions, then my first advice is to just use a normal ANOVA (`aov()` function in R). No need for the linear mixed models. To do so you must first convert the PAR values from continuous (numeric) to discrete (categorical). The `cut()` function is useful for converting numeric values into a predefined number of categories. Once your PAR values have been set to discrete levels, you should be able to run `aov(O2_normalized ~ condition*PAR*week, data = Alaria)` to get the stats you want. You can use `TukeyHSD()` on the output of that to get the case by case comparisons".

Alaria$PAR<-cut(Alaria$PAR,breaks=3)
Anova_Alaria_O2<-aov(O2_normalized ~ condition*PAR*week, data = Alaria)
TukeyHSD(Anova_Alaria_O2)
# p-value < 0.05 ? 
# C3:Week5-C1:TF (p=0.0387630)

Saccharina$PAR<-cut(Saccharina$PAR,breaks=3)
Anova_Saccharina_O2<-aov(O2_normalized ~ condition*PAR*week, data = Saccharina)
TukeyHSD(Anova_Saccharina_O2)

# p-value < 0.05 ? 
# Entre C3 et T0 (p=0418936)

Laminaria$PAR<-cut(Laminaria$PAR,breaks=3)
Anova_Laminaria_O2<-aov(O2_normalized ~ condition*PAR*week, data = Laminaria)
TukeyHSD(Anova_Laminaria_O2)
# p-value < 0.05 ? NEVER

## Statistics - old Version ####
# We want to compare each measurements of O2 synthesis mean between : conditions, replicates, species, weeks
# To do so we can use a linear mixed-effects model
# We can test 2 different models :
# the first one (HLM_O2) include the factor time (week) as a fixed factor i.e. a factor we wanna test

#Alaria<-Alaria[,-16]
#Alaria<-Alaria %>% distinct()

Alaria_stat_O2<-lmer(O2_normalized ~ week*condition + (1|replicate), data=Alaria)
Anova(Alaria_stat_O2)
emmeans(Alaria_stat_O2, list(pairwise ~ week*condition), adjust = "tukey")

Laminaria_stat_O2<-lmer(O2_normalized ~ week*condition + (1|replicate), data=Laminaria)
emmeans(Laminaria_stat_O2, list(pairwise ~ week*condition), adjust = "tukey")

Saccharina_stat_O2<-lmer(O2_normalized ~ week*condition + (1|replicate), data=Saccharina)
Saccharina_stat_O2<-glm(O2_normalized ~ week*condition, data=Saccharina)
emmeans(Saccharina_stat_O2, list(pairwise ~ week*condition), adjust = "tukey")

HLM_O2 <- lmer(Alaria ~ species*condition*PAR*week + (1|replicate), data=O2)
                                #fixed = factor to test + #random= factor not to test but could have an impact
# the second one (HLM_O2_2) include the factor time (week) also as a random factor i.e. a factor not to test but that could have an impact on the model
#HLM_O2_2 <- lmer(O2_normalized ~ species*condition*PAR*week + (1|replicate)+(1|week), data=O2)
# Then we calculate the AIC to choose the best model between these two.
#AIC(HLM_O2)
#AIC(HLM_O2_2)
# The first model (HLM_Table) has the lowest AIC, it's therefore the best model.
#rm(HLM_O2_2) # remove the 2nd model (the worst one)
# Let's now do an ANOVA on this model.
#Anova(HLM_O2)
# Chisq = F 
# df
#df.residual(HLM_O2)
# df : df, df residual
# On note : F(df,df residual)

# To localize in between wich group of data are the significant differences (if they are), we do post-hoc test (or multiple comparison test) of Tukey. This test can be used to determine significant differences between group means in an analysis of variance.
#emmeans(HLM_O2, list(pairwise ~ species*condition*PAR*week), adjust = "tukey")

# In our case, nothing is significative exept :
# LD T0 & LD C0 TF
# LD T0 & LD C2 TF
# in both cases : 1 individual pull the data (CO & C2 TF)
```

Observations:<br>
- The photosynthesis rate of SL does not change between conditions & within time<br>
- The photosynthesis rate of AE & LD seems maybe less stable within time (increase) but it's not significative & it's pretty similar between the different conditions.

```{r Total O2, echo=FALSE, warning=FALSE, message=FALSE, results=FALSE,fig.width=15,fig.height=10}
### Total within incubation ####
# First : remove outliers
O2<-O2[!O2$O2_normalized_PAR>0.1,]

# O2_mean & std calcul
O2_mean<-O2 %>%
  select(grp,condition,replicate,mesocosm,species,week,ID,Salinity,Temp,O2_normalized_PAR,std_normalized_2) %>%
  group_by(condition,species,week)%>%
  summarise(O2_mean = sum(O2_normalized_PAR)/length(O2_normalized_PAR))

std_O2_mean<-O2 %>%
  select(grp,condition,replicate,mesocosm,species,week,ID,Salinity,Temp,O2_normalized_PAR,std_normalized_2) %>%
  group_by(condition,species,week)%>%
  summarise(std_O2_mean = sqrt(mean((std_normalized_2)^2)))

O2_mean_incubation<-merge(O2_mean,std_O2_mean,by=c("species","condition","week"))

#Division by species
Alaria_mean<-O2_mean_incubation[O2_mean_incubation$species=="AE",]
Alaria_mean$condition_week<-paste(Alaria_mean$condition,Alaria_mean$week,sep="_")

Laminaria_mean<-O2_mean_incubation[O2_mean_incubation$species=="LD",]
Laminaria_mean$condition_week<-paste(Laminaria_mean$condition,Laminaria_mean$week,sep="_")

Saccharina_mean<-O2_mean_incubation[O2_mean_incubation$species=="SL",]
Saccharina_mean$condition_week<-paste(Saccharina_mean$condition,Saccharina_mean$week,sep="_")

# Define the order of apparition on the facet
Alaria_mean$condition_week <- fct_relevel(Alaria_mean$condition_week, c("T0_T0", "C0_Week2","C0_Week5","C0_TF","C1_Week2","C1_Week5","C1_TF","C2_Week2","C2_Week5","C2_TF","C3_Week2","C3_Week5","C3_TF"))
Laminaria$condition_week <- fct_relevel(Laminaria$condition_week, c("T0_T0", "C0_Week3","C0_TF","C1_Week3","C1_TF","C2_Week3","C2_TF","C3_Week3","C3_TF"))
Saccharina$condition_week <- fct_relevel(Saccharina$condition_week, c("T0_T0", "C0_Week1","C0_Week4","C0_TF","C1_Week1","C1_Week4","C1_TF","C2_Week1","C2_Week4","C2_TF","C3_Week1","C3_Week4","C3_TF"))


# AE
AE_plot_mean<-ggplot()+
  geom_point(Alaria,mapping=aes(y=O2_normalized_PAR,x=condition_week,colour=condition),size=3,alpha=0.5)+
  geom_errorbar(Alaria,mapping=aes(y=O2_normalized_PAR,x=condition_week,ymin=O2_normalized_PAR-std_normalized_2, ymax=O2_normalized_PAR+std_normalized_2,colour=condition),width=.2,position=position_dodge(0.05),alpha=0.5)+
  geom_point(Alaria_mean,mapping=aes(y=O2_mean,x=condition_week),alpha=1,size=3)+
  geom_errorbar(Alaria_mean,mapping=aes(y=O2_mean,x=condition_week, ymin=O2_mean-std_O2_mean, ymax=O2_mean+std_O2_mean), width=.2,position=position_dodge(0.05),alpha=1)+
    scale_colour_manual(values=c("#cccccc","#92c5de","#0571b0","#f4a582","#ca0020"))+
  ylab(bquote(bold(O[2] ("µmol O2.gDW-1.min-1.umol photons-1 m-2 min-1"))))+
  xlab("")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.06),expand = expansion(mult = c(0,0)))+
  scale_x_discrete(labels= c("T0","Week 2", "Week 5","TF","Week 2", "Week 5","TF","Week 2", "Week 5","TF","Week 2", "Week 5","TF"))+
  annotate("rect", xmin = 0, xmax = 1.5, ymin = -0.01, ymax = 0.06, alpha = .1)+
  annotate("rect", xmin = 1.5, xmax = 4.5, ymin = -0.01, ymax = 0.06, alpha = .4)+
  annotate("rect", xmin = 4.5, xmax = 7.5, ymin = -0.01, ymax = 0.06, alpha = .1)+
  annotate("rect", xmin = 7.5, xmax = 10.5, ymin = -0.01, ymax = 0.06, alpha = .4)+
  annotate("rect", xmin = 10.5, xmax = 13.5, ymin = -0.01, ymax = 0.06, alpha = .1)+
  annotate("text", x = 3 + 3*(0:3), y = 0.03, label = c("C0","C1","C2","C3"), size = 4.5)+labs(caption = "AE")

# LD
LD_plot_mean<-ggplot()+
  geom_point(Laminaria,mapping=aes(y=O2_normalized_PAR,x=condition_week,colour=condition),size=3,alpha=0.5)+
  geom_errorbar(Laminaria,mapping=aes(y=O2_normalized_PAR,x=condition_week,ymin=O2_normalized_PAR-std_normalized_2, ymax=O2_normalized_PAR+std_normalized_2,colour=condition),width=.2,position=position_dodge(0.05),alpha=0.5)+
  geom_point(Laminaria_mean,mapping=aes(y=O2_mean,x=condition_week),alpha=1,size=3)+
  geom_errorbar(Laminaria_mean,mapping=aes(y=O2_mean,x=condition_week, ymin=O2_mean-std_O2_mean, ymax=O2_mean+std_O2_mean), width=.2,position=position_dodge(0.05),alpha=1)+
    scale_colour_manual(values=c("#cccccc","#92c5de","#0571b0","#f4a582","#ca0020"))+
  ylab(bquote(bold(O[2] ("µmol O2.gDW-1.min-1.umol photons-1 m-2 min-1"))))+
  xlab("")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.06),expand = expansion(mult = c(0,0)))+
  scale_x_discrete(labels= c("T0","Week 3","TF","Week 3","TF","Week 3","TF","Week 3","TF"))+
  annotate("rect", xmin = 0, xmax = 1.5, ymin = -0.01, ymax = 0.06, alpha = .1)+
  annotate("rect", xmin = 1.5, xmax = 3.5, ymin = -0.01, ymax = 0.06, alpha = .4)+
  annotate("rect", xmin = 3.5, xmax = 5.5, ymin = -0.01, ymax = 0.06, alpha = .1)+
  annotate("rect", xmin = 5.5, xmax = 7.5, ymin = -0.01, ymax = 0.06, alpha = .4)+
  annotate("rect", xmin = 7.5, xmax = 9.5, ymin = -0.01, ymax = 0.06, alpha = .1)+
  annotate("text", x = 2.5 + 2*(0:3), y =  0.03, label = c("C0","C1","C2","C3"), size = 4.5)+labs(caption = "LD")

# SL
SL_plot_mean<-ggplot()+
  geom_point(Saccharina,mapping=aes(y=O2_normalized_PAR,x=condition_week,colour=condition),size=3,alpha=0.5)+
  geom_errorbar(Saccharina,mapping=aes(y=O2_normalized_PAR,x=condition_week,ymin=O2_normalized_PAR-std_normalized_2, ymax=O2_normalized_PAR+std_normalized_2,colour=condition),width=.2,position=position_dodge(0.05),alpha=0.5)+
  geom_point(Saccharina_mean,mapping=aes(y=O2_mean,x=condition_week),alpha=1,size=3)+
  geom_errorbar(Saccharina_mean,mapping=aes(y=O2_mean,x=condition_week, ymin=O2_mean-std_O2_mean, ymax=O2_mean+std_O2_mean), width=.2,position=position_dodge(0.05),alpha=1)+
    scale_colour_manual(values=c("#cccccc","#92c5de","#0571b0","#f4a582","#ca0020"))+
  ylab(bquote(bold(O[2] ("µmol O2.gDW-1.min-1.umol photons-1 m-2 min-1"))))+
  xlab("")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.06),expand = expansion(mult = c(0,0)))+
  scale_x_discrete(labels= c("T0","Week 1", "Week 4","TF","Week 1", "Week 4","TF","Week 1", "Week 4","TF","Week 1", "Week 4","TF"))+
  annotate("rect", xmin = 0, xmax = 1.5, ymin = -0.01, ymax = 0.06, alpha = .1)+
  annotate("rect", xmin = 1.5, xmax = 4.5, ymin = -0.01, ymax = 0.06, alpha = .4)+
  annotate("rect", xmin = 4.5, xmax = 7.5, ymin = -0.01, ymax = 0.06, alpha = .1)+
  annotate("rect", xmin = 7.5, xmax = 10.5, ymin = -0.01, ymax = 0.06, alpha = .4)+
  annotate("rect", xmin = 10.5, xmax = 13.5, ymin = -0.01, ymax = 0.06, alpha = .1)+
  annotate("text", x = 3 + 3*(0:3), y = 0.03, label = c("C0","C1","C2","C3"), size = 4.5)+
  labs(caption = "SL")


### Total within conditions ####
#O2_mean_condition<-O2 %>%
#  select(grp,condition,replicate,mesocosm,species,O2_normalized_PAR,std_normalized_2) %>%
#  group_by(condition,species)%>%
#  summarise(O2_mean = sum(O2_normalized_PAR)/length(O2_normalized_PAR))

#std_O2_mean_condition<-O2 %>%
#  select(grp,condition,replicate,mesocosm,species,O2_normalized_PAR,std_normalized_2) %>%
#  group_by(condition,species)%>%
#  summarise(std_O2_mean = sqrt(mean((std_normalized_2)^2)))
#
#O2_mean_condition<-merge(O2_mean_condition,std_O2_mean_condition,by=c("species","condition"))


#Alaria_mean_condition<-O2_mean_condition[O2_mean_condition$species=="AE",]
#Laminaria_mean_condition<-O2_mean_condition[O2_mean_condition$species=="LD",]
#Saccharina_mean_condition<-O2_mean_condition[O2_mean_condition$species=="SL",]


# Define the order of apparition on the facet
#Alaria_mean_condition$condition <- fct_relevel(Alaria_mean_condition$condition, c("T0","C1","C2","C3"))
#Laminaria_mean_condition$condition_week <- fct_relevel(Laminaria_mean_condition$condition, c("T0","C1","C2","C3"))
#Saccharina_mean_condition$condition_week <- fct_relevel(Saccharina_mean_condition$condition, c("T0","C1","C2","C3"))

# AE
#AE_plot_total<-ggplot()+
#  geom_point(Alaria_mean_condition,mapping=aes(y=O2_mean,x=condition,colour=condition),alpha=1,size=3)+
#  geom_errorbar(Alaria_mean_condition,mapping=aes(y=O2_mean,x=condition, ymin=O2_mean-std_O2_mean, ymax=O2_mean+std_O2_mean), width=.2,position=position_dodge(0.05),alpha=1)+
#  scale_colour_manual(values=c("#cccccc","#92c5de","#0571b0","#f4a582","#ca0020"))+
#  ylab(bquote(bold(O[2] ("µmol O2.gDW-1.min-1.umol photons-1 m-2 min-1"))))+
#  xlab("")+
#  theme_fira()+
#  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
#        axis.text = element_text(size = rel(1.5)),
#        axis.text.x = element_text(angle = 60,vjust = 0.5),
#        strip.text.x = element_text(size = rel(1.5),face="bold"),
#        legend.position="none")+
#  scale_y_continuous(limits=c(-0.01,0.06),expand = expansion(mult = c(0,0)))+
#  labs(caption = "AE")

# et un boxplot ? 
give.n <- function(x){
   return(c(y = mean(x), label = length(x)))
}

AE_plot_total<-ggplot()+
  geom_boxplot(aes(y=O2_normalized_PAR,x=condition,colour=condition),data=Alaria)+
  scale_colour_manual(values=c("#cccccc","#92c5de","#0571b0","#f4a582","#ca0020"))+
  stat_summary(aes(y=0.03,x=condition),colour="black",data=Alaria,fun.data = give.n, geom = "text",size=8)+
  ylab(bquote(bold(O[2] ("µmol O2.gDW-1.min-1.umol photons-1 m-2 min-1"))))+
  xlab("")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.06),expand = expansion(mult = c(0,0)))+
  labs(caption = "AE")

LD_plot_total<-ggplot()+
  geom_boxplot(aes(y=O2_normalized_PAR,x=condition,colour=condition),data=Laminaria)+
  scale_colour_manual(values=c("#cccccc","#92c5de","#0571b0","#f4a582","#ca0020"))+
  stat_summary(aes(y=0.03,x=condition),colour="black",data=Laminaria,fun.data = give.n, geom = "text",size=8)+
  ylab(bquote(bold(O[2] ("µmol O2.gDW-1.min-1.umol photons-1 m-2 min-1"))))+
  xlab("")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.06),expand = expansion(mult = c(0,0)))+
  labs(caption = "LD")

Saccharina<-Saccharina[!Saccharina$O2_normalized_PAR>0.1,]
SL_plot_total<-ggplot()+
  geom_boxplot(aes(y=O2_normalized_PAR,x=condition,colour=condition),data=Saccharina)+
  #geom_jitter(aes(y=O2_normalized_PAR,x=condition),data=Saccharina,color="black", size=0.4) +
  scale_colour_manual(values=c("#cccccc","#92c5de","#0571b0","#f4a582","#ca0020"))+
  stat_summary(aes(y=0.03,x=condition),colour="black",data=Saccharina,fun.data = give.n, geom = "text",size=8)+
  ylab(bquote(bold(O[2] ("µmol O2.gDW-1.min-1.umol photons-1 m-2 min-1"))))+
  xlab("")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        legend.position="none")+
  scale_y_continuous(limits=c(-0.01,0.06),expand = expansion(mult = c(0,0)))+
  labs(caption = "SL")

```

## 6° PI curves : $O_{2}$ vs. PAR <br>

The mesocosm PAR data are used here as a proxi of the actual PAR in the incubation chambers. Same filters have been used on the top of the mesocosm and the chambers (from the same condition). Depending on the hour of the day (i.e. shade/light) we used rather M0, M1 or M2 PAR data whichever best represent the same irradiance received by the chamber.

```{r PAR , echo=FALSE, warning=FALSE, message=FALSE, results=FALSE,fig.width=15,fig.height=6}
#PAR values are the interpolated values after erroneous values were removed
#10 min integrated values are averaged (mean) & converted in secs (divided by 10*60).

ggplot(O2,aes(y=O2_normalized,x=PAR,color=species))+
  geom_point(size=5)+ 
  facet_wrap(~condition)+
  labs(y="O2 (µmol.g(dw)-1.min-1)",x="PAR(sec-1)")+
  scale_colour_viridis_d("Condition")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), face = "bold"),
        axis.text = element_text(size = rel(1.5)),
        legend.title = element_text(size = rel(1.5), face = "bold"),
        legend.text = element_text(size = rel(1.5), face = "bold"),
        legend.key.size = unit(1.5, "lines"),
        strip.text.x = element_text(size = rel(1.5),face="bold"))

#ggdraw() +
 # draw_plot(plot_1)+
#  draw_image("/Users/anaislebrun/Desktop/These/Mesocosm experiment/O2/table.png",  x = -0.013, y = -0.25, scale = 0.28)

```

Observation: no shape of PI curves.  <br>
Explanation: Variations of PAR are too low within incubation too make the photosynthesis rate vary.


## 7° Chla <br>

Now let's look at the Chla data at T0 & TF in each condition.

```{r Chla , echo=FALSE, warning=FALSE, message=FALSE, results=FALSE,fig.width=15,fig.height=10}
Chla <- read_excel("/Users/anaislebrun/Desktop/These/Meso Tromso 2022/MHV_Tromso/data/CHLA-Tromso.xlsx", col_types = c("numeric","text","text","text","text","text",  "text","text","text","text", "text","text", "text", "text","numeric", "numeric", "text", "text"))

# Data manipulation ####
Chla_TF<-Chla[Chla$`sample type`=="TF",]
Chla_T0<-Chla[Chla$`sample type`=="T0",]
Chla<-rbind(Chla_TF,Chla_T0)
rm(Chla_TF,Chla_T0)

# Il y a t'il des outliers ? 
#Le test généralisé ESD (Extrem Studentized Deviation) de Rosner permet la détection simultanée d’un ou plusieurs #outliers et ne nécessite aucun paramétrage.
library(EnvStats)
library(ggpubr)
# the parameter k defines the number of potential outlier in a dataset, the default k value is 3
Chla_Alaria<-Chla[Chla$species=="AE",]

Chla_Alaria_T0<-Chla_Alaria[Chla_Alaria$treatment=="T0",]
rosnerTest(Chla_Alaria_T0$`Chla (µg.g)`, k = 1)$all.stats # 1 outlier : 271.7544
Chla_Alaria_T0<-Chla_Alaria_T0[!Chla_Alaria_T0$ID=="bis",]
shapiro.test(Chla_Alaria_T0$`Chla (µg.g)`) # Normal (pvalue>0.05)
ggqqplot(Chla_Alaria_T0$`Chla (µg.g)`)

Chla_Alaria_C0<-Chla_Alaria[Chla_Alaria$treatment=="C0",]
rosnerTest(Chla_Alaria_C0$`Chla (µg.g)`, k = 1)$all.stats # 420.93720 is an outlier
Chla_Alaria_C0<-Chla_Alaria_C0[!Chla_Alaria_C0$`Chla (µg.g)`>=400,]
shapiro.test(Chla_Alaria_C0$`Chla (µg.g)`) # OK Normal now
ggqqplot(Chla_Alaria_C0$`Chla (µg.g)`)

Chla_Alaria_C1<-Chla_Alaria[Chla_Alaria$treatment=="C1",]
rosnerTest(Chla_Alaria_C1$`Chla (µg.g)`, k = 1)$all.stats # no outlier
shapiro.test(Chla_Alaria_C1$`Chla (µg.g)`)  # OK Normal

Chla_Alaria_C2<-Chla_Alaria[Chla_Alaria$treatment=="C2",]
rosnerTest(Chla_Alaria_C2$`Chla (µg.g)`, k = 1)$all.stats # no outlier
shapiro.test(Chla_Alaria_C2$`Chla (µg.g)`) # OK Normal 
ggqqplot(Chla_Alaria_C2$`Chla (µg.g)`)

Chla_Alaria_C3<-Chla_Alaria[Chla_Alaria$treatment=="C3",]
rosnerTest(Chla_Alaria_C3$`Chla (µg.g)`, k = 1)$all.stats # no outlier
shapiro.test(Chla_Alaria_C3$`Chla (µg.g)`) # OK Normal
ggqqplot(Chla_Alaria_C3$`Chla (µg.g)`)

# Rbind
Chla_Alaria<-rbind(Chla_Alaria_T0,Chla_Alaria_C0,Chla_Alaria_C1,Chla_Alaria_C2,Chla_Alaria_C3)
rm(Chla_Alaria_T0,Chla_Alaria_C0,Chla_Alaria_C1,Chla_Alaria_C2,Chla_Alaria_C3)

# Saccharina
Chla_Saccharina<-Chla[Chla$species=="SL",]
Chla_Saccharina_T0<-Chla_Saccharina[Chla_Saccharina$treatment=="T0",]
rosnerTest(Chla_Saccharina_T0$`Chla (µg.g)`, k = 1)$all.stats  # no outlier
shapiro.test(Chla_Saccharina_T0$`Chla (µg.g)`) # Normal
ggqqplot(Chla_Saccharina_T0$`Chla (µg.g)`)

Chla_Saccharina_C0<-Chla_Saccharina[Chla_Saccharina$treatment=="C0",]
rosnerTest(Chla_Saccharina_C0$`Chla (µg.g)`, k = 1)$all.stats  # no outlier
shapiro.test(Chla_Saccharina_C0$`Chla (µg.g)`) #Normal

Chla_Saccharina_C1<-Chla_Saccharina[Chla_Saccharina$treatment=="C1",]
rosnerTest(Chla_Saccharina_C1$`Chla (µg.g)`, k = 3)$all.stats #   no outlier
shapiro.test(Chla_Saccharina_C1$`Chla (µg.g)`) #Normal
ggqqplot(Chla_Saccharina_C1$`Chla (µg.g)`)

Chla_Saccharina_C2<-Chla_Saccharina[Chla_Saccharina$treatment=="C2",]
rosnerTest(Chla_Saccharina_C2$`Chla (µg.g)`, k = 1)$all.stats  # no outlier
shapiro.test(Chla_Saccharina_C2$`Chla (µg.g)`) # OK Normal now
ggqqplot(Chla_Saccharina_C2$`Chla (µg.g)`)

Chla_Saccharina_C3<-Chla_Saccharina[Chla_Saccharina$treatment=="C3",]
rosnerTest(Chla_Saccharina_C3$`Chla (µg.g)`, k = 1)$all.stats  # 104.50361 is an outlier
Chla_Saccharina_C3<-Chla_Saccharina_C3[!Chla_Saccharina_C3$`Chla (µg.g)`>=100,]
shapiro.test(Chla_Saccharina_C3$`Chla (µg.g)`) # OK Normal now
ggqqplot(Chla_Saccharina_C3$`Chla (µg.g)`)

# Rbind
Chla_Saccharina<-rbind(Chla_Saccharina_T0,Chla_Saccharina_C0,Chla_Saccharina_C1,Chla_Saccharina_C2,Chla_Saccharina_C3)
rm(Chla_Saccharina_T0,Chla_Saccharina_C0,Chla_Saccharina_C1,Chla_Saccharina_C2,Chla_Saccharina_C3)

# Laminaria
Chla_Laminaria<-Chla[Chla$species=="LD",]

Chla_Laminaria_T0<-Chla_Laminaria[Chla_Laminaria$treatment=="T0",]
rosnerTest(Chla_Laminaria_T0$`Chla (µg.g)`, k = 1)$all.stats  # no outlier
shapiro.test(Chla_Laminaria_T0$`Chla (µg.g)`) # Normal
ggqqplot(Chla_Laminaria_T0$`Chla (µg.g)`)

Chla_Laminaria_C0<-Chla_Laminaria[Chla_Laminaria$treatment=="C0",]
rosnerTest(Chla_Laminaria_C0$`Chla (µg.g)`, k = 1)$all.stats  # no outlier
shapiro.test(Chla_Laminaria_C0$`Chla (µg.g)`) # OK Normal
ggqqplot(Chla_Laminaria_C0$`Chla (µg.g)`)

Chla_Laminaria_C1<-Chla_Laminaria[Chla_Laminaria$treatment=="C1",]
rosnerTest(Chla_Laminaria_C1$`Chla (µg.g)`, k = 1)$all.stats # no outlier
shapiro.test(Chla_Laminaria_C1$`Chla (µg.g)`) # not Normal
ggqqplot(Chla_Laminaria_C1$`Chla (µg.g)`)

Chla_Laminaria_C2<-Chla_Laminaria[Chla_Laminaria$treatment=="C2",]
rosnerTest(Chla_Laminaria_C2$`Chla (µg.g)`, k = 1)$all.stats # no outlier
shapiro.test(Chla_Laminaria_C2$`Chla (µg.g)`) # OK Normal
ggqqplot(Chla_Laminaria_C2$`Chla (µg.g)`)

Chla_Laminaria_C3<-Chla_Laminaria[Chla_Laminaria$treatment=="C3",]
rosnerTest(Chla_Laminaria_C3$`Chla (µg.g)`, k = 1)$all.stats # no outlier
shapiro.test(Chla_Laminaria_C3$`Chla (µg.g)`) # OK Normal
ggqqplot(Chla_Laminaria_C3$`Chla (µg.g)`)
# no outlier with Laminaria

rm(Chla_Laminaria_T0,Chla_Laminaria_C0,Chla_Laminaria_C1,Chla_Laminaria_C2,Chla_Laminaria_C3)

Chla<-rbind(Chla_Saccharina,Chla_Laminaria,Chla_Alaria)

give.n <- function(x){
   return(c(y = mean(x), label = length(x)))
}

# PLOTS 
# Define the order of apparition of the condition (x axis)
Chla$treatment <- fct_relevel(Chla$treatment, c("T0", "C0","C1","C2","C3"))

Chla_plot<-ggplot(Chla,aes(y=`Chla (µg.g)`,x=treatment,fill=treatment))+
  geom_boxplot(outlier.alpha = 0)+
  theme_fira()+
  geom_jitter(shape = 21,aes(fill=treatment),color="black",size=3)+
  facet_wrap(~species,scales='free')+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  scale_color_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0),colour="black",data=Chla,fun.data = give.n, geom = "text",size=8)+
  theme(axis.title = element_text(size = rel(1.5), face = "bold", hjust=0.5),
        axis.text = element_text(size = rel(1.5)),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  ylab(bquote('Chl a '(µg.FW^-1)))+
  xlab(bquote('conditions'))+
  scale_y_continuous(limits = c(0, 110))

jpeg(filename = "figures/Chla/Chla_plot.jpeg",width=950, height=650)
Chla_plot
dev.off()

Pheo_plot<-ggplot(Chla,aes(y=`Pheo (µg.g)`,x=treatment,fill=treatment))+
  geom_boxplot(outlier.alpha = 0)+
  theme_fira()+
  geom_jitter(shape = 21,aes(fill=treatment),color="black",size=3)+
  facet_wrap(~species,scales='free')+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  scale_color_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0),colour="black",data=Chla,fun.data = give.n, geom = "text",size=8)+
  theme(axis.title = element_text(size = rel(1.5), face = "bold", hjust=0.5),
        axis.text = element_text(size = rel(1.5)),
        strip.text.x = element_text(size = rel(1.5),face="bold"),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  ylab(bquote('Pheopigments '(µg.FW^-1)))+
  xlab(bquote('conditions'))+
  scale_y_continuous(limits = c(0, 290))

jpeg(filename = "figures/Chla/Pheo_plot.jpeg",width=950, height=650)
Pheo_plot
dev.off()

jpeg(filename = "figures/Chla/Chla_Pheo_plots.jpeg",width=950, height=1300)
ggarrange(Chla_plot,Pheo_plot,
          ncol = 1, nrow = 2,common.legend = TRUE)
dev.off()
# Statistics ####
Anova_Chla<-aov(`Chla (µg.g)` ~ treatment*species, data = Chla)
TukeyHSD(Anova_Chla)
# p-value < 0.05 :
# All species combined: 
#           diff        lwr        upr     p adj
#C3-T0 -35.0535233 -53.26311 -16.8439369 0.0000069
#C3-C1 -24.1152426 -44.27651  -3.9539704 0.0108818

#AE:
#                   diff        lwr        upr     p adj
#C3:AE-T0:AE -49.34868666 -87.938717 -10.7586568 0.0021466
#C3:AE-C2:AE -34.37548857 -77.520454   8.7694764 0.2754528


#SL
#                   diff        lwr        upr     p adj
#C3:SL-T0:SL -49.72725072 -90.658158  -8.7963430 0.0047080

#LD : no significative difference

```

## 10° C/N <br>

```{r C/N, echo=FALSE, warning=FALSE, message=FALSE, results=FALSE,fig.width=15,fig.height=10}
CHN <- read_excel("data/CHN-TROMSO.xlsx", 
     col_types = c("text", "text", "text", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric"))

CHN<-inner_join(CHN, Chla, by=c("ID","species"))

# Search for outliers in C/N :
# AE:
CHN_AE<-CHN[CHN$species=="AE",]
CHN_AE_C0<-CHN_AE[CHN_AE$treatment=="C0",]
rosnerTest(CHN_AE_C0$`C/N`, k = 1)$all.stats # 10.78064 is an outlier
CHN_AE_C0<-CHN_AE_C0[!CHN_AE_C0$ID=="12",]
shapiro.test(CHN_AE_C0$`C/N`) # Normal

CHN<-CHN[!CHN$ID=="12",]

#LD
CHN_LD<-CHN[CHN$species=="LD",]
CHN_LD_C3<-CHN_LD[CHN_LD$treatment=="C3",]
rosnerTest(CHN_LD_C3$`C/N`, k = 2)$all.stats # 0.1632123 & 3.9744147 are outliers, they both correspond to ID 141
CHN_LD_C3<-CHN_LD_C3[!CHN_LD_C3$ID=="141",]
shapiro.test(CHN_LD_C3$`C/N`) # Normal

CHN<-CHN[!CHN$ID=="141",]

# Search for outliers in C & N separated :
# Let's start with C
# AE
# C0
rosnerTest(CHN_AE_C0$C_1mg, k = 1)$all.stats #64.51351 is an outlier
CHN_AE_C0<-CHN_AE_C0[!CHN_AE_C0$ID=="1",]
shapiro.test(CHN_AE_C0$C_1mg) # Normal

CHN<-CHN[!CHN$ID=="1",]

#C3
CHN_AE_C3<-CHN_AE[CHN_AE$treatment=="C3",]
rosnerTest(CHN_AE_C3$C_1mg, k = 1)$all.stats #  217.3729 is an outlier
CHN_AE_C3<-CHN_AE_C3[!CHN_AE_C3$ID=="54",]
shapiro.test(CHN_AE_C3$C_1mg) # Normal

CHN<-CHN[!CHN$ID=="54",]

# LD
CHN_LD_C2<-CHN_LD[CHN_LD$treatment=="C2",]
rosnerTest(CHN_LD_C2$C_1mg, k = 1)$all.stats #  no outlier
shapiro.test(CHN_LD_C2$C_1mg) # Normal
 
# SL
# T0
CHN_SL<-CHN[CHN$species=="SL",]
CHN_SL_T0<-CHN_SL[CHN_SL$treatment=="T0",]
rosnerTest(CHN_SL_T0$C_1mg, k = 1)$all.stats # 443.8972 is an outlier
CHN_SL_T0<-CHN_SL_T0[!CHN_SL_T0$ID=="T0 5",]
shapiro.test(CHN_SL_T0$C_1mg) #Normal

CHN<-CHN[!CHN$Samples.x=="SLT0 5",]

# C0
CHN_SL_C0<-CHN_SL[CHN_SL$treatment=="C0",]
rosnerTest(CHN_SL_C0$C_1mg, k = 1)$all.stats # 3662.235 is an outlier
CHN_SL_C0<-CHN_SL_C0[!CHN_SL_C0$ID=="109",]
shapiro.test(CHN_SL_C0$C_1mg) #Normal

CHN<-CHN[!CHN$ID=="109",]

# C2
CHN_SL_C2<-CHN_SL[CHN_SL$treatment=="C2",]
rosnerTest(CHN_SL_C2$C_1mg, k = 1)$all.stats # no outlier
shapiro.test(CHN_SL_C2$C_1mg) #Normal

# What about N ? 
# AE C2
CHN_AE_C2<-CHN_AE[CHN_AE$treatment=="C2",]
rosnerTest(CHN_AE_C2$N_1mg, k = 1)$all.stats # no outlier
shapiro.test(CHN_AE_C2$C_1mg) # Normal

# SL C0
rosnerTest(CHN_SL_C0$N_1mg, k = 1)$all.stats # no outlier

give.n <- function(x){
   return(c(y = mean(x), label = length(x)))
}
  
#boxplot C/N
CN<-ggplot(CHN,aes(y=`C/N`,x=treatment,fill=treatment))+
  geom_boxplot(outlier.alpha = 0)+
  geom_jitter(shape = 21,aes(fill=treatment),color="black",size=3)+
  facet_wrap(~species)+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=10,x=treatment),colour="black",data=CHN,fun.data = give.n, geom = "text",size=10)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  ylab(bquote("C/N"))+
  xlab(bquote('conditions'))

jpeg(filename = "figures/CN/CN.jpeg",width=950, height=650)
CN
dev.off()

#boxplot C
C<-ggplot(CHN,aes(y=C_1mg,x=treatment,fill=treatment))+
  geom_boxplot(outlier.alpha = 0)+
  geom_jitter(shape = 21,aes(fill=treatment),color="black",size=3)+
  facet_wrap(~species)+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  ylab(bquote('C'(mg.g^-1,DW)))+
  xlab(bquote('conditions'))

jpeg(filename = "figures/CN/C.jpeg",width=950, height=650)
C
dev.off()
#boxplot N
N<-ggplot(CHN,aes(y=N_1mg,x=treatment,fill=treatment))+
  geom_boxplot(outlier.alpha = 0)+
  geom_jitter(shape = 21,aes(fill=treatment),color="black",size=3)+
  facet_wrap(~species)+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  ylab(bquote('N'(mg.g^-1,DW)))+
  xlab(bquote('conditions'))
jpeg(filename = "figures/CN/N.jpeg",width=950, height=650)
N
dev.off()

jpeg(filename = "figures/CN/CN_C_N.jpeg",width=950, height=1300)
ggarrange(CN,C,N,
          ncol = 1, nrow = 3,common.legend = TRUE)
dev.off()
# Statistics C/N
Anova_CN<-aov(`C/N` ~ treatment*species, data = CHN)
TukeyHSD(Anova_CN)
# No significative difference between treatments within each species
# interesting :
#                  diff        lwr        upr     p adj
#C3:AE-C2:AE  6.13485741  -0.3752215 12.64493636 0.0842364 
Anova_C<-aov(C_1mg ~ treatment*species, data = CHN)
TukeyHSD(Anova_C)
# No significative difference between treatments within each species
# interesting :
#                  diff        lwr        upr     p adj
#C3:AE-C1:AE   67.6917804   -3.246368 138.629929 0.0758831
Anova_N<-aov(N_1mg ~ treatment*species, data = CHN)
TukeyHSD(Anova_N)
# No significative difference between treatments within each species

```

## 11° Diving PAM <br>

```{r PAM, echo=FALSE, warning=FALSE, message=FALSE, results=FALSE,fig.width=15,fig.height=10}
#### KELP ####
Kelp_Pam <- read_excel("data/Kelp_Pam.xlsx", col_types = c("date", 
     "text", "text", "text", "text", "text", 
     "numeric", "numeric", "numeric", "numeric", 
     "numeric", "numeric", "text"))
give.n <- function(x){
   return(c(y = mean(x), label = length(x)))
}

# All period merged
Kelp_Pam_plot<-ggplot(Kelp_Pam,aes(y=`Fv/Fm`,x=treatment,fill=treatment))+
  geom_boxplot(outlier.alpha = 0)+
  geom_jitter(shape = 21,color="black",size=3)+
  facet_wrap(~species)+
  scale_fill_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0.4,x=treatment),colour="black",data=Kelp_Pam,fun.data = give.n, geom = "text",size=10)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
   ylab(bquote(F[v]/F[m]))+
  labs(x="conditions")

jpeg(filename = "figures/PAM/Kelp_Pam_alperiod_plot.jpeg",width=950, height=650)
Kelp_Pam_plot
dev.off()

Kelp_Pam$group<-paste0(Kelp_Pam$treatment,Kelp_Pam$Date,sep="_")
Kelp_Pam$Date<-as.POSIXct(Kelp_Pam$Date,format="%Y-%M-%D")

Kelp_Pam_alongtime_plot<-ggplot(Kelp_Pam,aes(y=`Fv/Fm`,x=Date,color=treatment))+
  geom_jitter(shape = 16,size=3,alpha=0.8)+
  #geom_smooth(se=F,size=2,alpha=0.5)+
  geom_boxplot(aes(x=Date,group=group,fill=treatment),color="black",outlier.alpha = 0)+
  facet_wrap(species~.,ncol=1)+
  scale_fill_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  scale_color_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
   ylab(bquote(F[v]/F[m]))+
  #scale_x_continuous(breaks=c("2022-07-02 UTC","2022-07-07 UTC","2022-07-11 UTC","2022-07-14 UTC","2022-07-18 UTC","2022-07-21 UTC","2022-07-22 UTC")+
  labs(x="conditions")


# to do :
# changer les stick x : mettre 1 axe par date (donc 7 tick)
# ploter la température (sur un autre graph ? ou par dessus ?)

jpeg(filename = "figures/PAM/Kelp_Pam_alongtime_plot.jpeg",width=950, height=650)
Kelp_Pam_alongtime_plot
dev.off()

# Is there outlier ? 
library(EnvStats)
library(ggpubr)
# ALARIA ####
AE_PAM<-Kelp_Pam[Kelp_Pam$species=="Alaria",]

AE_PAM_C0<-AE_PAM[AE_PAM$treatment=="C0",]
#AE_PAM_C0_day1<-AE_PAM_C0[AE_PAM_C0$Sampling=="exp_day1",]
rosnerTest(AE_PAM_C0$`Fv/Fm`, k = 1)$all.stats # 1 outlier
AE_PAM_C0<-AE_PAM_C0[!AE_PAM_C0$`Fv/Fm`==0.624,]
shapiro.test(AE_PAM_C0$`Fv/Fm`) # Normal (pvalue>0.05)
ggqqplot(AE_PAM_C0$`Fv/Fm`)

AE_PAM_C2<-AE_PAM[AE_PAM$treatment=="C2",]
AE_PAM_C2_day1<-AE_PAM_C2[AE_PAM_C2$Sampling=="exp_day1",]
rosnerTest(AE_PAM_C2_day1$`Fv/Fm`, k = 2)$all.stats # no outlier 
shapiro.test(AE_PAM_C2_day1$`Fv/Fm`) # not Normal (pvalue<0.05)
ggqqplot(AE_PAM_C2_day1$`Fv/Fm`) #0.390 seems to be an outlier, what if we compare with all the pam data of Alaria ?
rosnerTest(AE_PAM_C2$`Fv/Fm`, k = 2)$all.stats #2 outliers : 0.390 & 0.623
shapiro.test(AE_PAM_C2$`Fv/Fm`) # not normal
ggqqplot(AE_PAM_C2$`Fv/Fm`) # indeed, 2 outLIERS
AE_PAM_C2<-AE_PAM_C2[!AE_PAM_C2$`Fv/Fm`==0.390,]
AE_PAM_C2<-AE_PAM_C2[!AE_PAM_C2$`Fv/Fm`==0.623,]

AE_PAM_C1<-AE_PAM[AE_PAM$treatment=="C1",]
ggqqplot(AE_PAM_C1$`Fv/Fm`) 
rosnerTest(AE_PAM_C1$`Fv/Fm`, k = 1)$all.stats #0.647 is an outlier
AE_PAM_C1<-AE_PAM_C1[!AE_PAM_C1$`Fv/Fm`==0.647,]

AE_PAM_C3<-AE_PAM[AE_PAM$treatment=="C3",]
ggqqplot(AE_PAM_C3$`Fv/Fm`) 
rosnerTest(AE_PAM_C3$`Fv/Fm`, k = 1)$all.stats #no outlier

# Rbind
AE_PAM<-rbind(AE_PAM_C0,AE_PAM_C1,AE_PAM_C2,AE_PAM_C3)
rm(AE_PAM_C0,AE_PAM_C1,AE_PAM_C2,AE_PAM_C3)
# LAMINARIA ####
LD_PAM<-Kelp_Pam[Kelp_Pam$species=="Laminaria",]

LD_PAM_C0<-LD_PAM[LD_PAM$treatment=="C0",]
ggqqplot(LD_PAM_C0$`Fv/Fm`)
rosnerTest(LD_PAM_C0$`Fv/Fm`, k = 2)$all.stats # 2 outliers:  0.473 & 0.478
LD_PAM_C0<-LD_PAM_C0[!LD_PAM_C0$`Fv/Fm`==0.473,]
LD_PAM_C0<-LD_PAM_C0[!LD_PAM_C0$`Fv/Fm`==0.478,]
shapiro.test(LD_PAM_C0$`Fv/Fm`) # Normal (pvalue>0.05)
ggqqplot(LD_PAM_C0$`Fv/Fm`)

LD_PAM_C1<-LD_PAM[LD_PAM$treatment=="C1",]
rosnerTest(LD_PAM_C1$`Fv/Fm`, k = 1)$all.stats # 1 outlier : 0.528
LD_PAM_C1<-LD_PAM_C1[!LD_PAM_C1$`Fv/Fm`==0.528,]
shapiro.test(LD_PAM_C1$`Fv/Fm`) # Normal (pvalue>0.05)
ggqqplot(LD_PAM_C1$`Fv/Fm`)

LD_PAM_C2<-LD_PAM[LD_PAM$treatment=="C2",]
rosnerTest(LD_PAM_C2$`Fv/Fm`, k = 2)$all.stats # 2 outliers : 0.523 & 0.577
LD_PAM_C2<-LD_PAM_C2[!LD_PAM_C2$`Fv/Fm`==0.523,]
LD_PAM_C2<-LD_PAM_C2[!LD_PAM_C2$`Fv/Fm`==0.577,]
shapiro.test(LD_PAM_C2$`Fv/Fm`) # Normal (pvalue>0.05)
ggqqplot(LD_PAM_C2$`Fv/Fm`)


LD_PAM_C3<-LD_PAM[LD_PAM$treatment=="C3",]
rosnerTest(LD_PAM_C3$`Fv/Fm`, k = 1)$all.stats # 1 outlier : 0.409
LD_PAM_C3<-LD_PAM_C3[!LD_PAM_C3$`Fv/Fm`==0.409,]
shapiro.test(LD_PAM_C3$`Fv/Fm`) # Normal (pvalue>0.05)
ggqqplot(LD_PAM_C3$`Fv/Fm`)

LD_PAM<-rbind(LD_PAM_C0,LD_PAM_C1,LD_PAM_C2,LD_PAM_C3)
rm(LD_PAM_C0,LD_PAM_C1,LD_PAM_C2,LD_PAM_C3)

# SACCHARINA ####

SL_PAM<-Kelp_Pam[Kelp_Pam$species=="Saccharina",]

SL_PAM_C0<-SL_PAM[SL_PAM$treatment=="C0",]
ggqqplot(SL_PAM_C0$`Fv/Fm`)
rosnerTest(SL_PAM_C0$`Fv/Fm`, k = 1)$all.stats # no outlier
shapiro.test(SL_PAM_C0$`Fv/Fm`) # Normal (pvalue>0.05)

SL_PAM_C1<-SL_PAM[SL_PAM$treatment=="C1",]
ggqqplot(SL_PAM_C1$`Fv/Fm`)
rosnerTest(SL_PAM_C1$`Fv/Fm`, k = 1)$all.stats # no outlier
shapiro.test(SL_PAM_C1$`Fv/Fm`) # not Normal (pvalue>0.05)
# issue in one sampling day ?
SL_PAM_C1_day1<-SL_PAM_C1[SL_PAM_C1$Sampling=="T0",]
ggqqplot(SL_PAM_C1_day1$`Fv/Fm`) # ok no outlier

SL_PAM_C2<-SL_PAM[SL_PAM$treatment=="C2",]
ggqqplot(SL_PAM_C2$`Fv/Fm`)
rosnerTest(SL_PAM_C2$`Fv/Fm`, k = 1)$all.stats # no outlier
shapiro.test(SL_PAM_C2$`Fv/Fm`)

SL_PAM_C3<-SL_PAM[SL_PAM$treatment=="C3",]
ggqqplot(SL_PAM_C3$`Fv/Fm`)
rosnerTest(SL_PAM_C3$`Fv/Fm`, k = 1)$all.stats # no outlier
shapiro.test(SL_PAM_C3$`Fv/Fm`)

# NO outlier with SL
SL_PAM<-rbind(SL_PAM_C0,SL_PAM_C1,SL_PAM_C2,SL_PAM_C3)
rm(SL_PAM_C0,SL_PAM_C1,SL_PAM_C2,SL_PAM_C3)

Kelp_PAM_no_outlier<-rbind(AE_PAM,LD_PAM,SL_PAM)

# PLOTs without the outliers: 
Kelp_PAM_no_outlier_no_T0<-Kelp_PAM_no_outlier[!Kelp_PAM_no_outlier$Sampling=="T0",]
Kelp_Pam_plot_no_outlier<-ggplot(Kelp_PAM_no_outlier_no_T0,aes(y=`Fv/Fm`,x=treatment,fill=treatment))+
  geom_boxplot(outlier.alpha = 0)+
  geom_jitter(shape = 21,color="black",size=3)+
  facet_wrap(~species)+
  scale_fill_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0.4,x=treatment),colour="black",data=Kelp_Pam,fun.data = give.n, geom = "text",size=10)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
   ylab(bquote(F[v]/F[m]))+
  labs(x="conditions")

jpeg(filename = "figures/PAM/Kelp_Pam_alperiod_plot_no_outlier.jpeg",width=950, height=650)
Kelp_Pam_plot_no_outlier
dev.off()


Kelp_Pam_alongtime_plot_no_outlier<-ggplot(Kelp_PAM_no_outlier,aes(y=`Fv/Fm`,x=Date,color=treatment))+
  geom_jitter(shape = 16,size=3,alpha=0.8)+
  #geom_smooth(se=F,size=2,alpha=0.5)+
  geom_boxplot(aes(x=Date,group=group,fill=treatment),color="black",outlier.alpha = 0)+
  facet_wrap(species~.,ncol=1)+
  scale_fill_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  scale_color_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
   ylab(bquote(F[v]/F[m]))+
  labs(x="conditions")

# to do :
# changer les stick x : mettre 1 axe par date (donc 7 tick)
# ploter la température (sur un autre graph ? ou par dessus ?)

jpeg(filename = "figures/PAM/Kelp_Pam_alongtime_plot_no_outlier.jpeg",width=950, height=650)
Kelp_Pam_alongtime_plot_no_outlier
dev.off()

#### CORALLINE ####
Coralline_PAM <- read_excel("data/Coralline_PAM_data.xlsx")
give.n <- function(x){
   return(c(y = mean(x), label = length(x)))
}

# All period merged
Coralline_Pam_allperiod_plot<-ggplot(Coralline_PAM,aes(y=`Fv/Fm`,x=treatment,fill=treatment))+
  geom_boxplot(outlier.alpha = 0)+
  geom_jitter(shape = 21,color="black",size=3)+
  scale_fill_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0.4,x=treatment),colour="black",data=Coralline_PAM,fun.data = give.n, geom = "text",size=10)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
   ylab(bquote(F[v]/F[m]))+
  labs(x="conditions")

jpeg(filename = "figures/PAM/Coralline_Pam_allperiod_plot.jpeg",width=950, height=650)
Coralline_Pam_allperiod_plot
dev.off()

Coralline_PAM$group<-paste0(Coralline_PAM$treatment,Coralline_PAM$Date,sep="_")

Coralline_PAM_alongtime_plot<-ggplot(Coralline_PAM,aes(y=`Fv/Fm`,x=Date,color=treatment))+
  geom_jitter(shape = 16,size=3,alpha=0.8)+
  #geom_smooth(se=F,size=2,alpha=0.5)+
  geom_boxplot(aes(x=Date,group=group,fill=treatment),color="black",outlier.alpha = 0)+
  scale_fill_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  scale_color_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
   ylab(bquote(F[v]/F[m]))+
  labs(x="conditions")

jpeg(filename = "figures/PAM/Coralline_PAM_alongtime_plot.jpeg",width=950, height=650)
Coralline_PAM_alongtime_plot
dev.off()

# is there any outlier ?
Coralline_PAM_C0<-Coralline_PAM[Coralline_PAM$treatment=="C0",]
ggqqplot(Coralline_PAM_C0$`Fv/Fm`)
rosnerTest(Coralline_PAM_C0$`Fv/Fm`, k = 1)$all.stats # no outlier
shapiro.test(Coralline_PAM_C0$`Fv/Fm`) # Normal

Coralline_PAM_C1<-Coralline_PAM[Coralline_PAM$treatment=="C1",]
ggqqplot(Coralline_PAM_C1$`Fv/Fm`)
rosnerTest(Coralline_PAM_C1$`Fv/Fm`, k = 1)$all.stats # no outlier
shapiro.test(Coralline_PAM_C1$`Fv/Fm`) #Normal

Coralline_PAM_C2<-Coralline_PAM[Coralline_PAM$treatment=="C2",]
ggqqplot(Coralline_PAM_C2$`Fv/Fm`)
rosnerTest(Coralline_PAM_C2$`Fv/Fm`, k = 1)$all.stats # 1 outlier : 0.707 
Coralline_PAM_C2<-Coralline_PAM_C2[!Coralline_PAM_C2$`Fv/Fm`==0.707 ,]
shapiro.test(Coralline_PAM_C2$`Fv/Fm`) 

Coralline_PAM_C3<-Coralline_PAM[Coralline_PAM$treatment=="C3",]
ggqqplot(Coralline_PAM_C3$`Fv/Fm`)
rosnerTest(Coralline_PAM_C3$`Fv/Fm`, k = 1)$all.stats # no outlier
shapiro.test(Coralline_PAM_C3$`Fv/Fm`) #Normal

Coralline_PAM<-Coralline_PAM[!Coralline_PAM$`Fv/Fm`==0.707 ,]

# Plots without the outlier:
Coralline_Pam_allperiod_plot_no_outlier<-ggplot(Coralline_PAM,aes(y=`Fv/Fm`,x=treatment,fill=treatment))+
  geom_boxplot(outlier.alpha = 0)+
  geom_jitter(shape = 21,color="black",size=3)+
  scale_fill_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0.4,x=treatment),colour="black",data=Coralline_PAM,fun.data = give.n, geom = "text",size=10)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
   ylab(bquote(F[v]/F[m]))+
  labs(x="conditions")

jpeg(filename = "figures/PAM/Coralline_Pam_allperiod_plot_no_outlier.jpeg",width=950, height=650)
Coralline_Pam_allperiod_plot_no_outlier
dev.off()

Coralline_PAM_alongtime_plot_no_outlier<-ggplot(Coralline_PAM,aes(y=`Fv/Fm`,x=Date,color=treatment))+
  geom_jitter(shape = 16,size=3,alpha=0.8)+
  #geom_smooth(se=F,size=2,alpha=0.5)+
  geom_boxplot(aes(x=Date,group=group,fill=treatment),color="black",outlier.alpha = 0)+
  scale_fill_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  scale_color_manual(values=c("#92c5de","#E48121","#FC1D28","#901C21"))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
   ylab(bquote(F[v]/F[m]))+
  labs(x="conditions")

jpeg(filename = "figures/PAM/Coralline_PAM_alongtime_plot_no_outlier.jpeg",width=950, height=650)
Coralline_PAM_alongtime_plot_no_outlier
dev.off()
```

## 8° Growth <br>
```{r Growth , echo=FALSE, warning=FALSE, message=FALSE, results=FALSE,fig.width=15,fig.height=10}
# KELP ####
Growth <-  read_excel("data/GROWTH.xlsx", 
     col_types = c("text", "numeric", "text", 
         "text", "text", "text", "numeric", 
         "numeric", "text", "text", "text"))

# Data manipulation ####
#Growth<- na.omit(Growth) #Remove NA
Growth$treatment <- fct_relevel(Growth$treatment, c("C0","C1","C2","C3"))

# Plots  ####
give.n <- function(x){
   return(c(y = mean(x), label = length(x)))
}


# Mean for barplot
#Growth_mean<-Growth %>%
#  drop_na(Growth_rate)%>%
#  group_by(species,treatment) %>%
#  summarise(mean_growth=mean(Growth_rate))%>%
#  ungroup()

#Growth<-inner_join(Growth,Growth_mean,by=c("species","treatment"))

# std for barplot
#Growth_sd<-Growth %>%
#  drop_na(Growth_rate)%>%
#  group_by(species,treatment) %>%
#  summarise(sd_growth=sd(Growth_rate))%>%
#  ungroup()

#Growth<-inner_join(Growth,Growth_sd,by=c("species","treatment"))


Growth_plot<-ggplot(Growth,aes(x=treatment,fill=treatment))+
  #geom_bar(aes(y=mean_growth),stat='identity',color="black", position=position_dodge()) +
  #geom_errorbar(aes(ymin=mean_growth-sd_growth, ymax=mean_growth+sd_growth),width=.2,position=position_dodge(.9))+
  geom_boxplot(aes(y=Growth_rate),outlier.alpha = 0)+
  geom_jitter(shape = 21,aes(y=Growth_rate,fill=treatment),color="black",size=3)+
  facet_wrap(~species)+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0.4,x=treatment),colour="black",data=Growth,fun.data = give.n, geom = "text",size=10)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  labs(y="Growth rate (cm/day)",x="conditions")

jpeg(filename = "figures/Growth/Growth_rate_kelp.jpeg",width=950, height=650)
Growth_plot
dev.off()

# Growth rate vary with total lenght, let's take this variable into account by creating a model
################ Based on a script of Daniel Liesner ##########
Kelp_ID <- read_excel("data/Kelp_ID.xlsx", 
     col_types = c("numeric", "text", "numeric", 
         "text", "text", "numeric", "numeric", 
         "numeric", "text", "text", "text"))
Growth_normalized<-merge(Kelp_ID,Growth,by="ID")
Growth_normalized$`Total lenght (cm)`
### visually identify effects of initial length (covariate) on growth rates
library(nlme)
library(ggu.base.fun)
# log transformation is necessary to look into a LINEAR model here
# It allows the residuals to be normaly distributed (see later)
Growth_normalized$lg_growth_rate<-log(Growth_normalized$Growth_rate)
Growth_normalized$lg_total_lenght<-log(Growth_normalized$`Total lenght (cm)`)

Growth_normalized <- Growth_normalized[!is.infinite(Growth_normalized$lg_growth_rate),] #remove inf values
Growth_normalized <- Growth_normalized[!is.na(Growth_normalized$lg_growth_rate),] # remove NA
length_lm <- lm(lg_growth_rate ~ lg_total_lenght,data=Growth_normalized)
plot(lg_growth_rate ~ lg_total_lenght,data=Growth_normalized)
abline(length_lm)
summary(length_lm)
# equation : log(y)=4.2797 + (-1.5663)*log(total_lenght) + 1.024
Growth_normalized$Normalized_growth_rate<-10^(4.2797 + (-1.5663)*Growth_normalized$lg_total_lenght + 1.024)

# normality of standardized model residuals
length_lm_std <- residuals(length_lm, type="pearson")
shapiro.test(length_lm_std) #p-value = 0.108, normality verified
qqnorm(length_lm_std)
qqline(length_lm_std)
hist(length.lm.std, xlab="standardized residuals")

# homogeneity of model variances
leveneTest(length.lm.std , group = Growth_normalized$lg_growth_rate) # Normal
leveneTest(length.lm.std , group = Growth_normalized$lg_total_lenght) # Normal

### ANOVA for the final model
anova(length_lm)
#Analysis of Variance Table
#Response: lg_growth_rate
#                 Df  Sum Sq Mean Sq F value    Pr(>F)    
#lg_total_lenght   1  32.777  32.777  31.274 1.081e-07 ***
#Residuals       145 151.971   1.048                      
#---
#Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

Normalized_growth_rate_kelp<-ggplot(Growth_normalized,aes(x=treatment,fill=treatment))+
  #geom_bar(aes(y=mean_growth),stat='identity',color="black", position=position_dodge()) +
  #geom_errorbar(aes(ymin=mean_growth-sd_growth, ymax=mean_growth+sd_growth),width=.2,position=position_dodge(.9))+
  geom_boxplot(aes(y=Normalized_growth_rate),outlier.alpha = 0)+
  geom_jitter(shape = 21,aes(y=Normalized_growth_rate,fill=treatment),color="black",size=3)+
  facet_wrap(~species)+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0.4,x=treatment),colour="black",data=Growth_normalized,fun.data = give.n, geom = "text",size=10)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  labs(y="Growth rate (cm/day)",x="conditions")

jpeg(filename = "figures/Growth/Normalized_growth_rate_kelp.jpeg",width=950, height=650)
Normalized_growth_rate_kelp
dev.off()

# CORALLINE ####
Corraline_growth <- read_excel("data/Corraline_growth.xlsx")
Corraline_growth$treatment <- fct_relevel(Corraline_growth$treatment, c("C0","C1","C2","C3"))

# Plots  ####
give.n <- function(x){
   return(c(y = mean(x), label = length(x)))
}

#The average composition of minerals in the shells is approximately 90 percent calcite and 10 percent aragonite (Hutchinson and O'Sullivan 2008).
Corraline_growth$density_T0 <- rho(S=33, T=Corraline_growth$T0_Temperature_BW, P=0)
Corraline_growth$dry_weight_T0 <- Corraline_growth$T0_Buyant_weight*(1-((Corraline_growth$density_T0/1000)*((2.93^-1)*0.1+((2.71^-1)*0.9)))) 

Corraline_growth$density_TF <- rho(S=33, T=Corraline_growth$TF_Temperature_BW, P=0)
Corraline_growth$dry_weight_TF <- Corraline_growth$TF_Buyant_weight*(1-((Corraline_growth$density_TF/1000)*((2.93^-1)*0.1+((2.71^-1)*0.9))))

Corraline_growth$delta_dry_weight<-Corraline_growth$dry_weight_TF-Corraline_growth$dry_weight_T0

# 8 outliers : -42.69, -39.48, -19.37
ggqqplot(Corraline_growth$delta_dry_weight)
shapiro.test(Corraline_growth$delta_dry_weight) # not normal
rosnerTest(Corraline_growth$delta_dry_weight, k = 8)$all.stats  # 8 outliers
Corraline_growth<-Corraline_growth[!Corraline_growth$Delta_BW==-42.69,]
Corraline_growth<-Corraline_growth[!Corraline_growth$ID==9,]
Corraline_growth<-Corraline_growth[!Corraline_growth$Delta_BW==-19.37,]
Corraline_growth<-Corraline_growth[!Corraline_growth$ID==70,]
Corraline_growth<-Corraline_growth[!Corraline_growth$ID==8,]
Corraline_growth<-Corraline_growth[!Corraline_growth$ID==69,]
Corraline_growth<-Corraline_growth[!Corraline_growth$ID==68,]
Corraline_growth<-Corraline_growth[!Corraline_growth$ID==74,]
shapiro.test(Corraline_growth$delta_dry_weight) # normal

Corraline_growth_plot<-ggplot(Corraline_growth,aes(x=treatment,fill=treatment))+
  #geom_bar(aes(y=mean_growth),stat='identity',color="black", position=position_dodge()) +
  #geom_errorbar(aes(ymin=mean_growth-sd_growth, ymax=mean_growth+sd_growth),width=.2,position=position_dodge(.9))+
  geom_boxplot(aes(y=delta_dry_weight),outlier.alpha = 0)+
  geom_jitter(shape = 21,aes(y=delta_dry_weight,fill=treatment),color="black",size=3)+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0.4,x=treatment),colour="black",data=Corraline_growth,fun.data = give.n, geom = "text",size=10)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  labs(y="Delta dry weight (g)",x="conditions")

jpeg(filename = "figures/Growth/Corraline_growth_plot.jpeg",width=950, height=650)
Corraline_growth_plot
dev.off()


# SNAILS ####
snails_growth <- read_excel("data/snails_growth.xlsx", 
     col_types = c("text", "numeric", "text", 
         "numeric", "numeric", "numeric", 
         "date", "numeric", "numeric", "numeric", 
         "numeric", "text", "date", "text", "text", 
         "numeric", "numeric", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "text", "numeric"))

snails_growth$density_T0 <- rho(S=33, T=snails_growth$T0_Temperature_BW, P=0)
snails_growth$dry_weight_T0 <- snails_growth$T0_Buyant_weight*(1-((snails_growth$density_T0/1000)*((2.93^-1)*0.1+((2.71^-1)*0.9)))) 

snails_growth$density_TF <- rho(S=33, T=snails_growth$TF_Temperature_BW, P=0)
snails_growth$dry_weight_TF <- snails_growth$TF_Buyant_weight*(1-((snails_growth$density_TF/1000)*((2.93^-1)*0.1+((2.71^-1)*0.9))))

snails_growth$delta_dry_weight<-snails_growth$dry_weight_TF-snails_growth$dry_weight_T0

ggqqplot(snails_growth$delta_dry_weight)
shapiro.test(snails_growth$delta_dry_weight) # not normal
rosnerTest(snails_growth$delta_dry_weight, k = 6)$all.stats  # 11 outliers
snails_growth$ID_color<-paste(snails_growth$ID,snails_growth$Color,sep="_")
snails_growth<-snails_growth[!snails_growth$ID_color=="12_White",]
snails_growth<-snails_growth[!snails_growth$ID_color=="17_Red",]
snails_growth<-snails_growth[!snails_growth$ID_color=="8_Gold",]
snails_growth<-snails_growth[!snails_growth$ID_color=="9_White",]
snails_growth<-snails_growth[!snails_growth$ID_color=="7_Red",]
snails_growth<-snails_growth[!snails_growth$ID_color=="13_White",]
snails_growth<-snails_growth[!snails_growth$ID_color=="11_White",]
snails_growth<-snails_growth[!snails_growth$ID_color=="5_Red",]
snails_growth<-snails_growth[!snails_growth$ID_color=="14_Blue",]
snails_growth<-snails_growth[!snails_growth$ID_color=="14_Red",]
snails_growth<-snails_growth[!snails_growth$ID_color=="5_Gold",]
shapiro.test(snails_growth$delta_dry_weight) # normal

Snails_growth_plot<-ggplot(snails_growth,aes(x=treatment,fill=treatment))+
  #geom_bar(aes(y=mean_growth),stat='identity',color="black", position=position_dodge()) +
  #geom_errorbar(aes(ymin=mean_growth-sd_growth, ymax=mean_growth+sd_growth),width=.2,position=position_dodge(.9))+
  geom_boxplot(aes(y=delta_dry_weight),outlier.alpha = 0)+
  geom_jitter(shape = 21,aes(y=delta_dry_weight,fill=treatment),color="black",size=3)+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0.4,x=treatment),colour="black",data=snails_growth,fun.data = give.n, geom = "text",size=10)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  labs(y="Delta dry weight (g)",x="conditions")

jpeg(filename = "figures/Growth/Corraline_growth_plot.jpeg",width=950, height=650)
Snails_growth_plot
dev.off()

# MUSSELS ####

Mussels_growth <- read_excel("data/Mussels_growth.xlsx", 
     col_types = c("text", "text", "numeric", 
         "numeric", "date", "date", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric", "date", "text", "text", 
         "text"))

Mussels_growth$density_T0 <- rho(S=33, T=Mussels_growth$T0_Temperature_BW, P=0)
Mussels_growth$dry_weight_T0 <- Mussels_growth$T0_Buyant_weight*(1-((Mussels_growth$density_T0/1000)*((2.93^-1)*0.1+((2.71^-1)*0.9)))) 

Mussels_growth$density_TF <- rho(S=33, T=Mussels_growth$TF_Temperature_BW, P=0)
Mussels_growth$dry_weight_TF <- Mussels_growth$TF_Buyant_weight*(1-((Mussels_growth$density_TF/1000)*((2.93^-1)*0.1+((2.71^-1)*0.9))))

Mussels_growth$delta_dry_weight<-Mussels_growth$dry_weight_TF-Mussels_growth$dry_weight_T0

ggqqplot(Mussels_growth$delta_dry_weight)
shapiro.test(Mussels_growth$delta_dry_weight) # not normal
rosnerTest(Mussels_growth$delta_dry_weight, k = 20)$all.stats  # 12 outliers
Mussels_growth$ID_color<-paste(Mussels_growth$ID,Mussels_growth$Color,sep="_")
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="12_White",]
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="17_Red",]
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="8_Gold",]
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="9_White",]
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="7_Red",]
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="13_White",]
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="11_White",]
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="5_Red",]
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="14_Blue",]
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="14_Red",]
Mussels_growth<-Mussels_growth[!Mussels_growth$ID_color=="5_Gold",]
shapiro.test(Mussels_growth$delta_dry_weight) # normal

ggplot(Mussels_growth ,aes(x=treatment,fill=treatment))+
  #geom_bar(aes(y=mean_growth),stat='identity',color="black", position=position_dodge()) +
  #geom_errorbar(aes(ymin=mean_growth-sd_growth, ymax=mean_growth+sd_growth),width=.2,position=position_dodge(.9))+
  geom_boxplot(aes(y=delta_dry_weight),outlier.alpha = 0)+
  geom_jitter(shape = 21,aes(y=delta_dry_weight,fill=treatment),color="black",size=3)+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  stat_summary(aes(y=0.4,x=treatment),colour="black",data=Mussels_growth ,fun.data = give.n, geom = "text",size=10)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  labs(y="Delta BW",x="conditions")
# URCHINS ####
urchins_biomass <- read_excel("data/urchins_biomass.xlsx", 
     col_types = c("text", "text", "numeric", 
         "numeric", "numeric", "numeric", 
         "numeric"))
urchins_biomass<-ggplot(urchins_biomass ,aes(x=treatment,fill=treatment))+
  #geom_bar(aes(y=mean_growth),stat='identity',color="black", position=position_dodge()) +
  #geom_errorbar(aes(ymin=mean_growth-sd_growth, ymax=mean_growth+sd_growth),width=.2,position=position_dodge(.9))+
  geom_boxplot(aes(y=Delta_BW_n,label=n_TF),outlier.alpha = 0)+
  geom_jitter(shape = 21,aes(y=Delta_BW_n,fill=treatment),color="black",size=3)+
  scale_fill_manual(values=c("#cccccc","#92c5de","#E48121","#FC1D28","#901C21"))+
  geom_label(aes(y=Delta_BW_n,label=n_TF))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA),
        legend.position="none")+
  labs(y="Delta BW",x="conditions")


jpeg(filename = "figures/Growth/urchins_biomass.jpeg",width=950, height=650)
urchins_biomass
dev.off()

```

Observations:  <br>
- LD: growth rate decrease within time (-> stat), no variation withing conditions <br>
- SL: growth rate stable in time in C0 vs. decrease within time in C2 & C3. For C3, the growth rate is higher than at the other conditions. <br>
Explanation: A +5°C enhances the growth rate of SL (C3) but low light & salinity limit the growth rate (C2) <br>
- AE: growth rate decrease within time (-> stat). At C2 the growth rate increased at TF. We do only have one point but giving the previous Chl a data, something might be happenning here. Let's do some bibliography of AE & her maybe love for low salinity. <br>




## 9° Growth vs Chla <br>
```{r Growth vs Chla, echo=FALSE, warning=FALSE, message=FALSE,results=FALSE, fig.width=15,fig.height=10}
Gr_Chla<-merge(Growth,Chla)
Alaria_Gr_Chla<-Gr_Chla[Gr_Chla$Species=="AE",]
Saccharina_Gr_Chla<-Gr_Chla[Gr_Chla$Species=="SL",]
Laminaria_Gr_Chla<-Gr_Chla[Gr_Chla$Species=="LD",]

AE_Gr_Chla<-ggplot(Alaria_Gr_Chla,aes(y=`Chla (µg.g)`,x=Growth_rate,colour=Condition))+
  geom_point(size=5)+ 
  scale_colour_viridis_d(direction=1)+
  labs(y="Growth rate (cm/day)",x="Chla (µg.g) ")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1), face = "bold"),
        axis.text = element_text(size = rel(0.95)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        legend.position="none")


SL_Gr_Chla<-ggplot(Saccharina_Gr_Chla,aes(y=`Chla (µg.g)`,x=Growth_rate,colour=Condition))+
  geom_point(size=5)+ 
  scale_colour_viridis_d(direction=1)+
  labs(y="Growth rate (cm/day)",x="Chla (µg.g) ")+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1), face = "bold"),
        axis.text = element_text(size = rel(0.95)),
        axis.text.x = element_text(angle = 60,vjust = 0.5),
        legend.position="none")

ggarrange(AE_Gr_Chla,SL_Gr_Chla,label=c("AE","SL"))
```
## 13° Temp,Sal,PAR <br>

```{r Temp,Sal,PAR, echo=FALSE, warning=FALSE, message=FALSE, results=FALSE,fig.width=15,fig.height=10}
PAR_alltogether <- read_excel("Desktop/These/Meso NYA 2021/O2/data/PAR_alltogether.xlsx", 
+     sheet = "All_together", col_types = c("date", 
+         "text", "text", "numeric"))

ggplot(data=PAR_alltogether)+
  geom_line(aes(x=DateTime_rounded,y=C0M0,colour=Mesocosm))+
  facet_wrap(~Condition)

ggplot(data=PAR_alltogether)+
  geom_line(aes(x=DateTime_rounded,y=log(C0M0),colour=Mesocosm),alpha=0.7)+
  #geom_point(aes(x=DateTime_rounded,y=log(C0M0),colour=Mesocosm),alpha=0.25)+
  facet_wrap(~Condition)+
  theme_fira()

SalinityTemp  <- read_excel("Desktop/These/Meso NYA 2021/O2/data/SalinityTemp.xlsx", col_types = c("date", "text", "text", "numeric","numeric"))
SalinityTemp$Meso<-paste("S",SalinityTemp$Mesocosm,sep="_")
coeff <- 2

ggplot(data=SalinityTemp)+
  geom_line(aes(x=Date,y=Temperature,color=Mesocosm),alpha=0.7)+
  geom_line(aes(x=Date,y=Salinity/coeff,color=Meso),alpha=0.7)+
  scale_color_manual(values=c("#79E671","#679E57","#3F6035","#92c5de","#0571b0","#0041B6"))+
  #scale_colour_manual(values=c("#92c5de","#0571b0","#0041B6"))+
  scale_y_continuous(
    # Features of the first axis
    name = "Temperature",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~.*coeff, name="Salinity"))+
  facet_wrap(~Condition)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(0.9)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA))+
  scale_x_datetime(date_breaks="10 days",limits=as.POSIXct(c("2021-06-30 22:01","2021-08-28 13:01")))

# 1 graph for Temp
ggplot(data=SalinityTemp)+
  annotate("rect", xmin = as.POSIXct("2021-06-30 22:01"), xmax = as.POSIXct("2021-07-16 00:01"), ymin = 2.5, ymax = 13, alpha = .2)+
  geom_line(aes(x=Date,y=Temperature,color=Condition),alpha=0.7)+
  scale_color_manual(values=c("#92c5de","#0571b0","#f4a582","#ca0020"))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(1.2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA))+
  scale_x_datetime(date_breaks="10 days",limits=as.POSIXct(c("2021-06-30 22:01","2021-08-28 13:01")))+
  scale_y_continuous(limits=c(2.5,13),expand = expansion(mult = c(0,0)))

# 1 graph for Salinity
ggplot(data=SalinityTemp)+
  annotate("rect", xmin = as.POSIXct("2021-06-30 22:01"), xmax = as.POSIXct("2021-07-16 00:01"), ymin = 19, ymax = 37, alpha = .2)+
  geom_line(aes(x=Date,y=Salinity,color=Condition),alpha=0.7)+
  scale_color_manual(values=c("#92c5de","#0571b0","#f4a582","#ca0020"))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(1.2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA))+
  scale_x_datetime(date_breaks="10 days",limits=as.POSIXct(c("2021-06-30 22:01","2021-08-28 13:01")))+
    scale_y_continuous(limits=c(19,37),expand = expansion(mult = c(0,0)))

# 1 graph for Irradiance

ggplot(data=PAR_alltogether)+
  geom_line(aes(x=DateTime_rounded,y=C0M0,color=Condition),alpha=0.7)+
  scale_color_manual(values=c("#92c5de","#0571b0","#f4a582","#ca0020"))+
  facet_wrap(~Condition)+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(0.9)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA))+
  scale_x_datetime(date_breaks="10 days",limits=as.POSIXct(c("2021-06-30 22:01","2021-08-28 13:01")))

# 1 graph for Irradiance in log
ggplot(data=PAR_alltogether,aes(x=DateTime_rounded,y=log(C0M0),color=Condition))+
  annotate("rect", xmin = as.POSIXct("2021-06-30 22:01"), xmax = as.POSIXct("2021-07-16 00:01"), ymin = -2.5, ymax = 7, alpha = .2)+
  geom_line(alpha=0.1)+
  geom_smooth(size=0.9)+
  #geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) +
  #stat_smooth(method=loess,size=1.2, span=.6)+
  scale_color_manual(values=c("#92c5de","#0571b0","#f4a582","#ca0020"))+
  theme_fira()+
  theme(axis.title = element_text(size = rel(1.5), hjust=0.5),
        axis.text = element_text(size = rel(1.2)),
        strip.text.x = element_text(size = rel(2)),
        panel.border = element_rect(colour = "black", fill=NA))+
  scale_x_datetime(date_breaks="10 days",limits=as.POSIXct(c("2021-06-30 22:01","2021-08-28 13:01")))+
  scale_y_continuous(limits=c(-2.5,7),expand = expansion(mult = c(0,0)))



```




